---
title: "ROTP Analyses"
author: "Jesse Barrera"
output: html_document
date: "2023-05-06"
---

```{r}


knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


# Load packages

```{r}

library (readr)
library(dplyr)
library(psych)
library(lubridate)
library(mice)
library(tidyr)
library(lme4)
library(jtools)
library(sjPlot)
library(ggplot2)
library(GGally)
library(haven)
library(stats)
library(mice)
library(broom.mixed)
library(utils)
library(ggeffects)

```

# Import data

```{r}

setwd("/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Deidentified Data")

rotp_merged <- read.csv("ROTP_Merged_Deidentified.csv")

biomarkers <- read.csv("H48_CRP_data_0_imputed.csv")

```

# Create a long dataframe of physio and non-physio data

## Remove unecessary columns

```{r}

rotp_behavioral <- rotp_merged %>% 
  select(-c(X))

```

## Create separate physio and non-physio dataframes

```{r}

rotp_physio <- rotp_behavioral %>% 
  select(contains("_physio")) %>% 
  select(!(contains("non"))) %>% 
  mutate(participant_id = as.factor(rotp_behavioral$participant_id),
         condition = as.factor(rotp_behavioral$condition_physio)) %>% 
  filter(!is.na(condition))

rotp_non_physio <- rotp_behavioral %>% 
  select(contains("non_physio")) %>% 
  mutate(participant_id = as.factor(rotp_behavioral$participant_id),
         condition = as.factor(rotp_behavioral$condition_non_physio))  %>% 
  filter(!is.na(condition))


```

## Create separate dataframes for each timepoint

```{r}

# Physio

rotp_physio_t5 <- rotp_physio %>% 
  select(contains("_t5")) %>% 
  mutate(participant_id = rotp_physio$participant_id,
         condition = rotp_physio$condition,
         timepoint = 5)

rotp_physio_t6 <- rotp_physio %>% 
  select(contains("_t6")) %>% 
  mutate(participant_id = rotp_physio$participant_id,
         condition = rotp_physio$condition,
         timepoint = 6)

rotp_physio_t7 <- rotp_physio %>% 
  select(contains("_t7")) %>% 
  mutate(participant_id = rotp_physio$participant_id,
         condition = rotp_physio$condition,
         timepoint = 7)

rotp_physio_t8 <- rotp_physio %>% 
  select(contains("_t8")) %>% 
  mutate(participant_id = rotp_physio$participant_id,
         condition = rotp_physio$condition,
         timepoint = 8)


# Non-Physio

rotp_non_physio_t5 <- rotp_non_physio %>% 
  select(contains("_t5")) %>% 
  mutate(participant_id = rotp_non_physio$participant_id,
         condition = rotp_non_physio$condition,
         timepoint = 5)

rotp_non_physio_t6 <- rotp_non_physio %>% 
  select(contains("_t6")) %>% 
  mutate(participant_id = rotp_non_physio$participant_id,
         condition = rotp_non_physio$condition,
         timepoint = 6)

rotp_non_physio_t7 <- rotp_non_physio %>% 
  select(contains("_t7")) %>% 
  mutate(participant_id = rotp_non_physio$participant_id,
         condition = rotp_non_physio$condition,
         timepoint = 7)

rotp_non_physio_t8 <- rotp_non_physio %>% 
  select(contains("_t8")) %>% 
  mutate(participant_id = rotp_non_physio$participant_id,
         condition = rotp_non_physio$condition,
         timepoint = 8)


```

## Rename variables

```{r}

# Physio

colnames(rotp_physio_t5) <-  gsub("_t5_physio", "", colnames(rotp_physio_t5))

colnames(rotp_physio_t6) <-  gsub("_t6_physio",  "", colnames(rotp_physio_t6))

colnames(rotp_physio_t7) <-  gsub("_t7_physio",  "", colnames(rotp_physio_t7))

colnames(rotp_physio_t8) <-  gsub("_t8_physio",  "", colnames(rotp_physio_t8))

# Non-Physio

colnames(rotp_non_physio_t5) <-  gsub("_t5_non_physio", "", colnames(rotp_non_physio_t5))

colnames(rotp_non_physio_t6) <-  gsub("_t6_non_physio",  "", colnames(rotp_non_physio_t6))

colnames(rotp_non_physio_t7) <-  gsub("_t7_non_physio",  "", colnames(rotp_non_physio_t7))

colnames(rotp_non_physio_t8) <-  gsub("_t8_non_physio",  "", colnames(rotp_non_physio_t8))

```

# Merge timepoints back together for physio and non-physio

```{r}

# Physio

rotp_physio_long <- bind_rows(rotp_physio_t5, rotp_physio_t6, rotp_physio_t7, rotp_physio_t8) %>% 
  mutate(branch = "physio",
         timepoint = as.factor(timepoint),
         cov_months_1 = as.factor(cov_months_1),
         cov_months_2 = as.factor(cov_months_2),
         cov_months_3 = as.factor(cov_months_3)) %>% 
  relocate(participant_id, .before = duration) %>% 
  relocate(timepoint, .after = participant_id) %>% 
  relocate(branch, .after = timepoint) %>% 
  relocate(condition, .after = branch) %>% 
  arrange(participant_id, timepoint)

# Non-Physio

rotp_non_physio_long <- bind_rows(rotp_non_physio_t5, rotp_non_physio_t6, rotp_non_physio_t7, rotp_non_physio_t8) %>% 
  mutate(branch = "non physio",
         timepoint = as.factor(timepoint),
         cov_months_1 = as.factor(cov_months_1),
         cov_months_2 = as.factor(cov_months_2),
         cov_months_3 = as.factor(cov_months_3)) %>% 
  relocate(participant_id, .before = duration) %>% 
  relocate(timepoint, .after = participant_id) %>% 
  relocate(branch, .after = timepoint) %>% 
   relocate(condition, .after = branch) %>% 
  arrange(participant_id, timepoint)

```

# Merge physio and non-physio into a single long dataframe

```{r}

rotp_behavioral_long <- bind_rows(rotp_physio_long, rotp_non_physio_long)

write.csv(rotp_behavioral_long, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Preprocessed Data/rotp_behavioral_long.csv")

```

## Make separate dataframe for physio analyses

```{r}

# Change behavioral df timepoints

rotp_behavioral_ajd_t5 <- rotp_behavioral_long %>% 
  filter(timepoint == 5) %>% 
  mutate(timepoint = 1) 

rotp_behavioral_ajd_t6 <- rotp_behavioral_long %>% 
  filter(timepoint == 6) %>% 
    mutate(timepoint = 1.5)

rotp_behavioral_ajd_t7 <- rotp_behavioral_long %>% 
  filter(timepoint == 7)  %>% 
    mutate(timepoint = 2)

rotp_behavioral_ajd_t8 <- rotp_behavioral_long %>% 
  filter(timepoint == 8) %>% 
    mutate(timepoint = 3)

rotp_behavioral_adj_123 <- bind_rows(rotp_behavioral_ajd_t5, rotp_behavioral_ajd_t7, rotp_behavioral_ajd_t8)

rotp_behavioral_adj <- bind_rows(rotp_behavioral_ajd_t5,rotp_behavioral_ajd_t6, rotp_behavioral_ajd_t7, rotp_behavioral_ajd_t8)

# Merge with biomarkers

rotp_behavioral_adj <- rotp_behavioral_adj %>% 
  mutate(timepoint = as.numeric(timepoint),
         participant_id = as.numeric(participant_id) + 500)

rotp_behavioral_physio_adj <- left_join(rotp_behavioral_adj, biomarkers, by = c("participant_id", "timepoint"))


write.csv(rotp_behavioral_physio_adj, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Deidentified Data/Behavioral_Physio_Long_Conditions.csv")
```


# Primary Analyses

## Examine correlations between CO mindset and outcome variables

```{r  setup, warning=FALSE}

# T5

rotp_behavioral_long_t5 <- rotp_behavioral_long %>% 
  filter(timepoint == 5)

ggpairs(rotp_behavioral_long_t5, 157:170, progress = FALSE)

# T6

rotp_behavioral_long_t6 <- rotp_behavioral_long %>% 
  filter(timepoint == 6)

ggpairs(rotp_behavioral_long_t6, 157:170, progress = FALSE) 

# T7

rotp_behavioral_long_t7 <- rotp_behavioral_long %>% 
  filter(timepoint == 7)

ggpairs(rotp_behavioral_long_t7, 157:170, progress = FALSE)

# T8

rotp_behavioral_long_t8 <- rotp_behavioral_long %>% 
  filter(timepoint == 8)

rotp_behavioral_long %>% 
  ggpairs(157:170, progress = FALSE)

ggpairs(rotp_behavioral_long_t8, 157:170, progress = FALSE)


```

## Examine correlations between CO mindset, PTG, depression, and biomarkers

```{r warning=FALSE}

# T5

rotp_behavioral_physio_adj_t1 <- rotp_behavioral_physio_adj %>% 
  filter(timepoint == 1) %>% 
  filter(branch == "physio") %>% 
  select(c(participant_id, timepoint, co_mindset, ptgi_full, phq_depression, IL6._Log2Transformed, IL10_Log2Transformed, IL1B_Log2Transformed, TNFA_Log2Transformed, CRP_Log2Transformed)) 


ggpairs(rotp_behavioral_physio_adj_t1, 3:10, progress = FALSE)

# T7

rotp_behavioral_physio_adj_t2 <- rotp_behavioral_physio_adj %>% 
  filter(timepoint == 2) %>% 
  filter(branch == "physio") %>% 
  select(c(participant_id, timepoint, co_mindset, ptgi_full, phq_depression, IL6._Log2Transformed, IL10_Log2Transformed, IL1B_Log2Transformed, TNFA_Log2Transformed, CRP_Log2Transformed)) 


ggpairs(rotp_behavioral_physio_adj_t2, 3:10, progress = FALSE)

# T8

rotp_behavioral_physio_adj_t3 <- rotp_behavioral_physio_adj %>% 
  filter(timepoint == 3) %>% 
  filter(branch == "physio") %>% 
  select(c(participant_id, timepoint, co_mindset, ptgi_full, phq_depression, IL6._Log2Transformed, IL10_Log2Transformed, IL1B_Log2Transformed, TNFA_Log2Transformed, CRP_Log2Transformed)) 


ggpairs(rotp_behavioral_physio_adj_t3, 3:10, progress = FALSE)


```


## CO Mindset - Mixed Model

```{r}

com.mm <- lmer(co_mindset ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(com.mm)

sjPlot::tab_model(com.mm)


# Plot model

plot_model(com.mm)

ggplot(rotp_behavioral_adj_123, aes(x = as.numeric(timepoint), y = co_mindset, color = condition)) +
geom_point(alpha = 0.5, size = 1, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Linear Mixed Effects Model of Catastrophes Mindset Across Time x Condition") +
  scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("CO Mindset (Mean)", limits = 1:7, labels = 1:7) +
theme_minimal()

View(rotp_behavioral_adj)

# Addtional plot models

ggplot(rotp_behavioral_adj_123, aes(x = timepoint, y = co_mindset, group = condition, color = condition)) +
geom_point() +
stat_summary(fun = median, geom = "line", size = 1.5) +
labs(title = "Catastrophes Mindset Across Time") +
scale_x_discrete("Timepoint", limits = 1:4, labels = 1:4) +
scale_y_discrete("CO Mindset", limits = 1:7, labels = 1:7) +
theme_minimal()





ggplot(rotp_behavioral_long, aes(x = as.numeric(timepoint), y = co_mindset, color = condition)) +
  geom_point() + 
  geom_smooth(method = "lm")

```

## PTG Full - Mixed Model

```{r}

rotp_behavioral_long_t5_t7_t8 <- rotp_behavioral_long %>% 
  filter(timepoint != 6)


ptg_full.mm <- lmer(ptgi_full ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_full.mm)

sjPlot::tab_model(ptg_full.mm)


# Plot model

plot_model(ptg_full.mm)

ggplot(rotp_behavioral_adj_123, aes(x = as.numeric(timepoint), y = ptgi_full, color = condition)) +
geom_point(alpha = 0.5, size = 1, position = position_jitter(width = 0.1)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Linear Mixed Effects Model of PTG Across Time x Condition") +
  scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("PTGI-Full (Mean)", limits = 0:5, labels = 0:5) +
theme_minimal()



# Additional plots

ggplot(rotp_behavioral_adj, aes(x = timepoint, y = ptgi_full, group = condition, color = condition)) +
geom_point() +
stat_summary(fun = median, geom = "line", size = 1.5) +
labs(title = "Post-Traumatic Growth Across Time") +
scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("PTGI-Full", limits = 0:5, labels = 0:5) +
theme_minimal()




```


## PTG Abridged - Mixed Model

```{r}

ptg_abridged.mm <- lmer(ptgi_abridged ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_abridged.mm)

sjPlot::tab_model(ptg_abridged.mm)


# Plot model

plot_model(ptg_abridged.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_abridged, color = condition)) + 
  geom_smooth(method = "lm")

```

PTGI Relationships Subscale - Mixed Model

```{r}

ptg_relationships.mm <- lmer(ptgi_relationships ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_relationships.mm)

sjPlot::tab_model(ptg_relationships.mm)


# Plot model

plot_model(ptg_relationships.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_relationships, color = condition)) +
  geom_boxplot() + 
  theme_bw()


```

PTGI Possibilities Subscale - Mixed Models

```{r}

ptg_possibilities.mm <- lmer(ptgi_possibilities ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_possibilities.mm)

sjPlot::tab_model(ptg_possibilities.mm)


# Plot model

plot_model(ptg_possibilities.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_possibilities, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

PTGI Strength Subscale - Mixed Models

```{r}

ptg_strength.mm <- lmer(ptgi_strength ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_strength.mm)

sjPlot::tab_model(ptg_strength.mm)

ggplot(rotp_behavioral_adj_123, aes(x = as.numeric(timepoint), y = ptgi_strength, color = condition)) +
geom_point(alpha = 0.5, size = 1, position = position_jitter(width = 0.2)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Linear Mixed Effects Model of Depression Across Time x Condition") +
  scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("PTGI - Strength", limits = 0:5, labels = 0:5) +
theme_minimal()



# Plot model



plot_model(ptg_strength.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_strength, color = condition)) +
  geom_boxplot() +
  theme_bw()


```

PTGI Appreciation - Mixed Model

```{r}

ptg_appreciation.mm <- lmer(ptgi_appreciation ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_appreciation.mm)

sjPlot::tab_model(ptg_appreciation.mm)


# Plot model

plot_model(ptg_appreciation.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_appreciation, color = condition)) +
  geom_boxplot() +
  theme_bw()


```

## PTGI Spiritual - Mixed Model

```{r}

ptg_spiritual.mm <- lmer(ptgi_spiritual ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long)

summ(ptg_spiritual.mm)

sjPlot::tab_model(ptg_spiritual.mm)


# Plot model

plot_model(ptg_spiritual.mm)

ggplot(rotp_behavioral_long, aes(x = timepoint, y = ptgi_spiritual, color = condition)) +
  geom_boxplot() +
  theme_bw()


```

# Positive Affect - Mixed Model

```{r}

pos_affect.mm <- lmer(pos_affect ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(pos_affect.mm)

sjPlot::tab_model(pos_affect.mm)


# Plot model

plot_model(pos_affect.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = pos_affect, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

# Negative Affect - Mixed Model

```{r}

neg_affect.mm <- lmer(neg_affect ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(neg_affect.mm)

sjPlot::tab_model(neg_affect.mm)


# Plot model

plot_model(neg_affect.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = neg_affect, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## PHQ Full - Mixed Model

```{r}


phq_full.mm <- lmer(phq_full ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(phq_full.mm)

sjPlot::tab_model(phq_full.mm)


# Plot model

plot_model(phq_full.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = phq_full, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## PHQ Anxiety - Mixed Model

```{r}


phq_anxiety.mm <- lmer(phq_anxiety ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(phq_anxiety.mm)

sjPlot::tab_model(phq_anxiety.mm)


# Plot model

plot_model(phq_anxiety.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = phq_anxiety, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## PHQ Depression - Mixed Model

```{r}


phq_depression.mm <- lmer(phq_depression ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(phq_depression.mm)

sjPlot::tab_model(phq_depression.mm)


# Plot model

plot_model(phq_depression.mm)

ggplot(rotp_behavioral_adj_123, aes(x = as.numeric(timepoint), y = phq_depression, color = condition)) +
geom_point(alpha = 0.3, size = 1, position = position_jitter(width = 0.1, height = 0.2)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Linear Mixed Effects Model of Depression Across Time x Condition") +
  scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("PHQ-Depression", limits = 0:6, labels = 0:6) +
theme_minimal()

  

# Additional Plots

# Create a scatterplot with lines connecting medians
ggplot(rotp_behavioral_adj, aes(x = timepoint, y = phq_depression, group = condition, color = condition)) +
geom_point() +
stat_summary(fun = mean, geom = "line", size = 1.5) +
labs(title = "Depression Across Time") +
scale_x_discrete("Timepoint", limits = 1:3, labels = 1:3) +
scale_y_discrete("PHQ-Depression", limits = 0:6, labels = 0:6) +
theme_minimal()






ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = phq_depression, color = condition)) +
  geom_boxplot() +
  theme_bw()



```

## Meaning Presence - Mixed Model

```{r}


meaning_presence.mm <- lmer(meaning_presence ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(meaning_presence.mm)

sjPlot::tab_model(meaning_presence.mm)

# Plot model

plot_model(meaning_presence.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = meaning_presence, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## Meaning Search - Mixed Model

```{r}


meaning_search.mm <- lmer(meaning_search ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(meaning_search.mm)

sjPlot::tab_model(meaning_search.mm)

# Plot model

plot_model(meaning_search.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = meaning_search, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## Resilience - Mixed Model

## Meaning Search - Mixed Model

```{r}


resilience.mm <- lmer(resilience ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8)

summ(resilience.mm)

sjPlot::tab_model(resilience.mm)

# Plot model

plot_model(resilience.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = resilience, color = condition)) +
  geom_boxplot() +
  theme_bw()

```

## Closeness

```{r}

closeness.mm <- (lmer(closeness ~ condition * timepoint + (1 | participant_id), 
                   data = rotp_behavioral_long_t5_t7_t8))

summ(closeness.mm)

sjPlot::tab_model(closeness.mm)

# Plot model

plot_model(closeness.mm)

ggplot(rotp_behavioral_long_t5_t7_t8, aes(x = timepoint, y = closeness, color = condition)) +
  geom_boxplot() +
  theme_bw()


```


```{r}

rotp_summaries_long <- rotp_behavioral_long %>% 
  select(c(participant_id, timepoint, condition, branch, ptgi_full:closeness))


write_sav(rotp_summaries_long, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Deidentified Data/ROTP_Summaries.sav")
```


Merge data long with physio

```{r}

physio_for_merge <- rotp_merged %>% 
  select(participant_id, )

```

# CRP/Depression Mediation

```{r}

library(lavaan)

# Create new dataset


crp_dep_med_model_df <- rotp_behavioral_physio_adj %>% 
  filter(timepoint == 3, branch == "physio") %>% 
  select(participant_id, timepoint, condition, phq_depression, CRP_Log2Transformed)

crp_dep_med_model <- '
             # mediator
             CRP_Log2Transformed ~ a*condition
             phq_depression ~ b*CRP_Log2Transformed
           
             # direct effect
             phq_depression ~  c*condition

           # indirect effect (a*b)
             ab := a*b

           # total effect
             total := c + (a*b)
             '
         
crp_dep_med <- sem(crp_dep_med_model, data = crp_dep_med_model_df, meanstructure = TRUE,
           se = "boot", bootstrap = 500)

summary(crp_dep_med, fit.measures=T, standardized=T, ci=TRUE)

```

# IL10/Depression Mediation

```{r}

library(lavaan)

# Create new dataset


IL10_dep_med_model_df <- rotp_behavioral_physio_adj %>% 
  filter(timepoint == 3, branch == "physio") %>% 
  select(participant_id, timepoint, condition, phq_depression, IL10_Log2Transformed)

IL10_dep_med_model <- '
             # mediator
             IL10_Log2Transformed ~ a*condition
             phq_depression ~ b*IL10_Log2Transformed
           
             # direct effect
             phq_depression ~  c*condition

           # indirect effect (a*b)
             ab := a*b

           # total effect
             total := c + (a*b)
             '
         
IL10_dep_med <- sem(IL10_dep_med_model, data = IL10_dep_med_model_df, meanstructure = TRUE,
           se = "boot", bootstrap = 500)

summary(IL10_dep_med, fit.measures=T, standardized=T, ci=TRUE)




```

# IL10/Depression Mediation (Change scores)


```{r}

library(lavaan)

# Create new dataset


IL10_dep_med_model_df <- rotp_behavioral_physio_adj %>% 
  filter((timepoint == 3 | timepoint == 1), branch == "physio") %>% 
  select(participant_id, timepoint, condition, phq_depression, IL10_Log2Transformed)

IL10_t1 <- IL10_dep_med_model_df %>% 
  filter(timepoint == 1)

IL10_t3 <- IL10_dep_med_model_df %>% 
  filter(timepoint == 3)

IL10_1_3 <- inner_join(IL10_t1, IL10_t3, by = "participant_id", suffix = c("_t1", "_t3")) %>% 
  mutate(depression_change = phq_depression_t3 - phq_depression_t1,
         IL10_change = IL10_Log2Transformed_t3 - IL10_Log2Transformed_t1)




IL10_1_3_model <- '
             # mediator
             IL10_change ~ a*condition_t3
             depression_change ~ b*IL10_change
           
             # direct effect
             depression_change ~  c*condition_t3

           # indirect effect (a*b)
             ab := a*b

           # total effect
             total := c + (a*b)
             '
         
IL10_1_3_model_med <- sem(IL10_1_3_model, data = IL10_1_3, meanstructure = TRUE,
           se = "boot", bootstrap = 500)

summary(IL10_1_3_model_med, fit.measures=T, standardized=T, ci=TRUE)

install.packages("semPlot")

library(semPlot)

semPaths(IL10_1_3_model_med, whatLabels = "std", style = "lisrel", layout = "tree",
         rotation = 2)


```

Experimenting with multiple imputation

```{r}

rotp_imputation <- rotp_summaries_long

imputed <- mice(rotp_imputation, maxit=0)

predictor_matrix <- imputed$predictorMatrix

meth <- imputed$method

imp2 <- mice(rotp_imputation, maxit = 5, 
             predictorMatrix = predictor_matrix, 
             method = meth, print =  FALSE)

fitimp <- with(imp2, lmer(closeness ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(co_mindset ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(ptgi_full ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(pos_affect ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(neg_affect ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(meaning_presence ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))


fitimp <- with(imp2, lmer(resilience ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))



fitimp <- with(imp2, lmer(closeness ~ condition * timepoint + (1 | participant_id)))

summary(pool(fitimp))





```







