---
title: "ROTP Longitudinal Preprocessing"
author: "Jesse Barrera, Rachael Yielder, Lexi Straube"
output: html_document
date: "2023-04-25"
---

# Load packages

```{r}

library (readr)
library(dplyr)
library(psych)
library(lubridate)
library(mice)

```

# Import raw data

```{r}

setwd("/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/COVID Longitudinal Preprocessing")


longitudinal_raw <- read.csv("Raw Data/Longitudinal_Raw.csv", na.strings = c("", " "))


longitudinal_id_key <- read.csv("ROTP_Longitudinal_ID_Key.csv")

```

# Combine raw data and id key 

```{r}

# Remove unecessary columns from ID Key

longitudinal_id_key <- longitudinal_id_key %>% 
  select(participant_id, email)

# Merge ID key with raw data

longitudinal_raw <- longitudinal_raw %>% 
  left_join(longitudinal_id_key, by = "participant_id") %>% 
  select(-c("participant_id"))

```

# Remove unecessary Qualtrics metadata

```{r}

longitudinal_raw <- longitudinal_raw %>% 
  select(-c("X.1":"recorded_date_t1",
            "X_t2":"recorded_date_t2",
            "X_t3":"recorded_date_t3",
            "start_date_t4":"user_language_t4"))

```

# Convert variables to factors or chars as appropriate

```{r}

# Consent

longitudinal_raw$consent_t2 <- gsub(as.character(1), "Agree", longitudinal_raw$consent_t2)

longitudinal_raw$consent_t3 <- gsub("1", "Agree", longitudinal_raw$consent_t3)

longitudinal_raw$consent_t4 <- gsub("1", "Agree", longitudinal_raw$consent_t4)


# Employment

longitudinal_raw$employment_status_t4 <- cut(as.numeric(longitudinal_raw$employment_status_t4), 8, c('Currently employed and working full time', "Currently employed and working part-time", "Not currently working/unemployed", "Student", "Full time childcare/homemaker", "Retired", "Disabled", "Other (please explain)"))

# Age

longitudinal_raw <- longitudinal_raw %>% 
  mutate(dem_age_t1 = as.numeric(dem_age_t1) + 2) %>% 
  rename("age_t1" = "dem_age_t1")

# Gender

longitudinal_raw <- longitudinal_raw %>% 
  rename("gender_t1" = "dem_gender_t1")

# Race/Ethnicity

longitudinal_raw <- longitudinal_raw %>% 
  rename("race_ethnicity_t1" = "dem_race_t1")

# Political Affiliation

longitudinal_raw <- longitudinal_raw %>% 
  rename("political_party_t1" = "dem_politic_t1")

# Education (recode into binary variable: more than high school/high school or below)

longitudinal_raw$dem_education_t1 <- gsub("Some high school", "HS or less", gsub("High school degree", "HS or less",
                                                                                 gsub("4-year college degree", "More than HS", gsub("Master's, doctoral, or professional degree", "More than HS", longitudinal_raw$dem_education_t1))))

longitudinal_raw <- longitudinal_raw %>% 
  rename("education_t1" = 'dem_education_t1')

# Income (recode to match T5 physio branch)

## Convert strings to numeric values

longitudinal_raw$income_t4 <- gsub("k", "000", gsub("K", "000", gsub("thousand", "000", 
                                                                     gsub("Thousand", "000", longitudinal_raw$income_t4))))

longitudinal_raw$income_t4 <- as.numeric(gsub("\\D", "", longitudinal_raw$income_t4))

str(longitudinal_raw$income_t4)

longitudinal_raw <- longitudinal_raw %>%   
  mutate(income_t4 = case_when(income_t4 > 150000 ~ "Greater than $150,000",
                               income_t4 <= 150000 & income_t4 > 50000 ~ "$50,000 - $150,000",
                               income_t4 <= 50000 ~ "$0 - $50,000"))

```

# Convert variables to integers as appropriate

```{r}

longitudinal_raw <- longitudinal_raw %>% 
  mutate(across(c('co_mindset_2_t4':'soc_sufficient_t4', 'income_t4'), as.numeric))

```

# Summary Scores

## Controllable Meta-Mindset

### Rescale and reverse-code items

```{r}

# Rescale items from a 1-6 to a 0-5 scale

longitudinal_raw <- longitudinal_raw %>% 
  mutate(across(c(cmm_1_t4:cmm_4_t4), ~.-1))

# Reverse code items

longitudinal_raw <- longitudinal_raw %>% 
  mutate(cmm_1_t4 = 5 - cmm_1_t4,
         cmm_2_t4 = 5 - cmm_2_t4,
         cmm_3_t4 = 5 - cmm_3_t4,
         cmm_4_t4 = 5 - cmm_4_t4)


```

### Calculate summary scores and alphas

```{r}

# Calculate summary score

longitudinal_raw <- longitudinal_raw %>% 
  mutate(cmm_t4 = rowMeans(select(.,cmm_1_t4:cmm_4_t4)))

# Calculate alpha

cmm_t4_df <- longitudinal_raw %>% 
  select(cmm_1_t4:cmm_4_t4)

psych::alpha(cmm_t4_df)

```

# Create dataframe with demographics and summary scores

```{r}

# Select columns

longitudinal_summaries_raw <- longitudinal_raw %>% 
  select(state_resid_t1, age_t1:political_party_t1, income_t4, employment_status_t4, cmm_t4, email)

# Rename columns to prepare for merge with physio and non-physio

colnames(longitudinal_summaries_raw) <- gsub("_t1", "", gsub("_t4", "", colnames(longitudinal_summaries_raw)))

```



# Write data to Box

```{r}

write.csv(longitudinal_summaries_raw, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/COVID Longitudinal Preprocessing/Preprocessed Data/Longitudinal_Summaries_Raw.csv")


write.csv(longitudinal_raw, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/COVID Longitudinal Preprocessing/Preprocessed Data/Longitudinal_Preprocessed.csv")

```





