---
title: "ROTP Non-Physio Preprocessing"
author: "Jesse Barrera"
date: "2/22/23"
output: html_document
---

# Load packages

```{r}

library (readr)
library(dplyr)
library(psych)
library(lubridate)
library(mice)
library(naniar)

```

# Import raw data

```{r}

# Set working directory


setwd("/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ROTP Non-Physio Preprocessing/Raw Data")

# Import raw non-physio data


t1_raw_non_physio <- read.csv("ROTP_Non_Physio_T1_Raw.csv", na.strings = c("", " "))

t2_raw_non_physio_int <- read.csv("ROTP_Non_Physio_T2_Raw_Int.csv", na.strings = c("", " "))

t2_raw_non_physio_con <- read.csv("ROTP_Non_Physio_T2_Raw_Con.csv", na.strings = c("", " "))

t3_raw_non_physio <- read.csv("ROTP_Non_Physio_T3_Raw.csv", na.strings = c("", " "))

t4_raw_non_physio <- read.csv("ROTP_Non_Physio_T4_Raw.csv", na.strings = c("", " "))


```

# Remove unecessary Qualtrics metadata

```{r}

# T1

t1_raw_non_physio <- t1_raw_non_physio %>% 
  select(-c(IPAddress, RecordedDate, ResponseId, RecipientLastName,
            RecipientFirstName, ExternalReference, DistributionChannel, UserLanguage))

t1_raw_non_physio <- t1_raw_non_physio[-c(1,2), ]


# T2

## Intervention

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  select(-c(IPAddress, RecordedDate, ResponseId, RecipientLastName,
            RecipientFirstName, ExternalReference, DistributionChannel, UserLanguage))

t2_raw_non_physio_int <- t2_raw_non_physio_int[-c(1,2), ]

## Control

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  select(-c(IPAddress, RecordedDate, ResponseId, RecipientLastName,
            RecipientFirstName, ExternalReference, DistributionChannel, UserLanguage))

t2_raw_non_physio_con <- t2_raw_non_physio_con[-c(1,2), ]

# T3

t3_raw_non_physio <- t3_raw_non_physio %>% 
  select(-c(IPAddress, RecordedDate, ResponseId, RecipientLastName,
            RecipientFirstName, ExternalReference, DistributionChannel, UserLanguage))

t3_raw_non_physio <- t3_raw_non_physio[-c(1,2), ]

# T4

t4_raw_non_physio <- t4_raw_non_physio %>% 
  select(-c(IPAddress, RecordedDate, ResponseId, RecipientLastName,
            RecipientFirstName, ExternalReference, DistributionChannel, UserLanguage))

t4_raw_non_physio <- t4_raw_non_physio[-c(1,2), ]

```

# Remove test participants

```{r}

# Remove participants who:
## Started before study was launched or after study closed
## Do not have a status of "IP Address"
## Have an email address corresponding with a member of the lab

## T1

t1_raw_non_physio <- t1_raw_non_physio %>% 
  arrange(mdy_hm(StartDate)) %>% 
  filter(Status == "0") %>% 
  filter((mdy_hm(StartDate) >= mdy_hm("11/7/22 6:00")) & 
           (mdy_hm(EndDate) <= mdy_hm("11/14/22 23:59"))) %>% 
  filter(!(RecipientEmail %in% c("zoehuml@stanford.edu", "crum@stanford.edu",  
                              "aliajcrum@gmail.com", "zoehuml1@gmail.com", 
                              "barreraj@stanford.edu", "klouis@stanford.edu", 
                              "lstraube@stanford.edu", "jzielke@stanford.edu",
                            "jbkaul@stanford.edu", "krise@stanford.edu"
                            , "kconte@stanford.edu", "megan92@stanford.edu", 
                              "kpags@stanford.edu")))

## T2

## Intervention

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  arrange(mdy_hm(StartDate)) %>% 
  filter(Status == "0") %>% 
  filter((mdy_hm(StartDate) >= mdy_hm("11/18/22 12:28")) & 
           (mdy_hm(EndDate) <= mdy_hm("12/8/22 23:59"))) %>% 
     filter(!(RecipientEmail %in% c("zoehuml@stanford.edu", "crum@stanford.edu",  
                              "aliajcrum@gmail.com", "zoehuml1@gmail.com", 
                              "barreraj@stanford.edu", "klouis@stanford.edu", 
                              "lstraube@stanford.edu", "jzielke@stanford.edu",
                            "jbkaul@stanford.edu", "krise@stanford.edu"
                            , "kconte@stanford.edu", "megan92@stanford.edu", 
                              "kpags@stanford.edu")))

## Control

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  arrange(mdy_hm(StartDate)) %>% 
  filter(Status == "0") %>% 
  filter((mdy_hm(StartDate) >= mdy_hm("11/18/22 12:26")) & 
           (mdy_hm(EndDate) <= mdy_hm("12/8/22 23:59"))) %>% 
     filter(!(RecipientEmail %in% c("zoehuml@stanford.edu", "crum@stanford.edu",  
                              "aliajcrum@gmail.com", "zoehuml1@gmail.com", 
                              "barreraj@stanford.edu", "klouis@stanford.edu", 
                              "lstraube@stanford.edu", "jzielke@stanford.edu",
                            "jbkaul@stanford.edu", "krise@stanford.edu"
                            , "kconte@stanford.edu", "megan92@stanford.edu", 
                              "kpags@stanford.edu")))


## T3

t3_raw_non_physio <- t3_raw_non_physio %>% 
  arrange(mdy_hm(StartDate)) %>% 
  filter(Status == "0") %>% 
  filter((mdy_hm(StartDate) >= mdy_hm("12/14/22 14:00")) & 
           (mdy_hm(EndDate) <= mdy_hm("12/29/22 23:59"))) %>% 
    filter(!(RecipientEmail %in% c("zoehuml@stanford.edu", "crum@stanford.edu",  
                              "aliajcrum@gmail.com", "zoehuml1@gmail.com", 
                              "barreraj@stanford.edu", "klouis@stanford.edu", 
                              "lstraube@stanford.edu", "jzielke@stanford.edu",
                            "jbkaul@stanford.edu", "krise@stanford.edu"
                            , "kconte@stanford.edu", "megan92@stanford.edu", 
                              "kpags@stanford.edu")))

## T4


t4_raw_non_physio <- t4_raw_non_physio %>% 
  arrange(mdy_hm(StartDate)) %>% 
  filter(Status == "0") %>% 
  filter((mdy_hm(StartDate) >= mdy_hm("2/23/23 05:00")) & 
           (mdy_hm(EndDate) <= mdy_hm("3/8/23 23:59"))) %>% 
    filter(!(RecipientEmail %in% c("zoehuml@stanford.edu", "crum@stanford.edu",  
                              "aliajcrum@gmail.com", "zoehuml1@gmail.com", 
                              "barreraj@stanford.edu", "klouis@stanford.edu", 
                              "lstraube@stanford.edu", "jzielke@stanford.edu",
                            "jbkaul@stanford.edu", "krise@stanford.edu"
                            , "kconte@stanford.edu", "megan92@stanford.edu", 
                              "kpags@stanford.edu")))

```

# Remove ineligible participants

## T1

### Remove T1 duplicates

```{r}

# Remove duplicate responses, prioritizing a) the more complete response, and b) the first response

t1_raw_non_physio <- t1_raw_non_physio %>% 
  arrange(desc(as.numeric(Progress)), mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)


```

### Did not consent

```{r}

t1_raw_non_physio <- t1_raw_non_physio %>% 
  filter(consent_pt_1 == "12")

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t3_raw_non_physio <- t3_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t4_raw_non_physio <- t4_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)


```


### Did not complete T1 survey

```{r}

t1_raw_non_physio <- t1_raw_non_physio %>% 
  filter(Finished == "1")

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t3_raw_non_physio <- t3_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t4_raw_non_physio <- t4_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)


```

### Took less than 1/3 of median time to complete T1 survey

```{r}

t1_raw_non_physio <- t1_raw_non_physio %>% 
  filter(as.numeric(Duration..in.seconds.) >= (median(as.numeric(t1_raw_non_physio$Duration..in.seconds.))/3))

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t3_raw_non_physio <- t3_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

t4_raw_non_physio <- t4_raw_non_physio %>% 
  filter(RecipientEmail %in% t1_raw_non_physio$RecipientEmail)

```

## T2

### Remove T2 duplicates

```{r}

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  arrange(desc(as.numeric(Progress)), mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  arrange(desc(as.numeric(Progress)), mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)

```


### Participant not successfully randomized

```{r}

# Make a list of all participants who were successfully randomized

## Add condition variable to T2 dataframes

t2_raw_non_physio_int <- t2_raw_non_physio_int %>% 
  mutate(Condition = "Intervention")

t2_raw_non_physio_con <- t2_raw_non_physio_con %>% 
  mutate(Condition = "Control")

t2_raw_non_physio <- bind_rows(t2_raw_non_physio_int, t2_raw_non_physio_con) %>% 
  arrange(mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)


# Filter out participants who were not successfully randomized

t1_raw_non_physio <- t1_raw_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio$RecipientEmail)

t3_raw_non_physio <- t3_raw_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio$RecipientEmail)

t4_raw_non_physio <- t4_raw_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio$RecipientEmail)

```

### Calculate T2 retention statistics for CONSORT purposes

```{r}

# Calculate total and by-condition completion rates for T2

t2_completed_non_physio_int <- t2_raw_non_physio_int %>% 
  filter(Finished == "1")

t2_completed_non_physio_con <- t2_raw_non_physio_con %>% 
  filter(Finished == "1")

```

## T3

### Remove T3 duplicates

```{r}

t3_raw_non_physio <- t3_raw_non_physio %>% 
  arrange(desc(as.numeric(Progress)), mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)

```

### Calculate T3 retention statistics for CONSORT purposes

```{r}
 
# Calculate total and by-condition completion rates for T3

t3_completed_non_physio <- t3_raw_non_physio %>% 
  filter(Finished == "1")

t3_completed_int <- t3_completed_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio_int$RecipientEmail) 

t3_completed_con <- t3_completed_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio_con$RecipientEmail)
```

## T4

### Remove T4 duplicates

```{r}

t4_raw_non_physio <- t4_raw_non_physio %>% 
  arrange(desc(as.numeric(Progress)), mdy_hm(StartDate)) %>% 
  distinct(RecipientEmail, .keep_all = TRUE)

```

### Calculate T4 retention statistics for CONSORT purposes

```{r}
 
# Calculate total and by-condition completion rates for T3

t4_completed_non_physio <- t4_raw_non_physio %>% 
  filter(Finished == "1")

t4_completed_int <- t4_completed_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio_int$RecipientEmail)

t4_completed_con <- t4_completed_non_physio %>% 
  filter(RecipientEmail %in% t2_raw_non_physio_con$RecipientEmail)

```


# Merge Data

## Add timepoint indicator to column names

```{r}

# T1

colnames(t1_raw_non_physio) <- gsub("_t1", "", gsub("_t2", "", gsub("_t3", "", gsub("_t4", "", colnames(t1_raw_non_physio)))))

colnames(t1_raw_non_physio) <- paste(colnames(t1_raw_non_physio), "t5", sep = "_") 

t1_raw_non_physio <- t1_raw_non_physio %>% 
  rename("RecipientEmail" = "RecipientEmail_t5")

# T2

colnames(t2_raw_non_physio) <- gsub("_t1", "", gsub("_t2", "", gsub("_t3", "", gsub("_t4", "", colnames(t2_raw_non_physio)))))

colnames(t2_raw_non_physio) <- paste(colnames(t2_raw_non_physio), "t6", sep = "_") 

t2_raw_non_physio <- t2_raw_non_physio %>% 
  rename("RecipientEmail" = "RecipientEmail_t6")

# T3

colnames(t3_raw_non_physio) <- gsub("_t1", "", gsub("_t2", "", gsub("_t3", "", gsub("_t4", "", colnames(t3_raw_non_physio)))))

colnames(t3_raw_non_physio) <- paste(colnames(t3_raw_non_physio), "t7", sep = "_") 

t3_raw_non_physio <- t3_raw_non_physio %>% 
  rename("RecipientEmail" = "RecipientEmail_t7")

# T4

colnames(t4_raw_non_physio) <- gsub("_t1", "", gsub("_t2", "", gsub("_t3", "", gsub("_t4", "", colnames(t4_raw_non_physio)))))

colnames(t4_raw_non_physio) <- paste(colnames(t4_raw_non_physio), "t8", sep = "_") 

t4_raw_non_physio <- t4_raw_non_physio %>% 
  rename("RecipientEmail" = "RecipientEmail_t8")


```


## Merge data in wide format

```{r}

# Merge T1 and T2 dataframes using left_join (retaining all rows from T1 and matching 
# rows from T2)

t1_t2_non_physio <- left_join(t1_raw_non_physio, t2_raw_non_physio, by = "RecipientEmail")

# Merge T3 and T4 dataframes using full_join (retaining all rows from T3 and T4)

t3_t4_non_physio <- full_join(t3_raw_non_physio, t4_raw_non_physio, by = "RecipientEmail")

# Merge all four timpeoints into a single dataframe using left_join 

non_physio_merged_raw <- left_join(t1_t2_non_physio, t3_t4_non_physio, by = "RecipientEmail")


```

# Add participant_id column 

```{r}

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(participant_id = sample(c(636:1150), nrow(non_physio_merged_raw), 
                                  replace = FALSE))


```

# Recode variables

## Convert chars to nums as necessary

```{r}

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c("Duration..in.seconds._t5",
                  "Finished_t5",
                  "prh_routine_t5",
                  "prh_income_t5",
                  "employment_t5",
                "prh_food_t5",
                "prh_housing_t5",
                "prh_medical_t5",
                "prh_mental_t5", 
                "prh_support_t5",
                "prh_stress_t5",
                "prh_discord_t5",
                "prh_care_t5",
                'prh_self_cov_t5',
                'cov_number_t5':'covid_sym_1_t5',
                'long_covid_t5',
                'prh_fam_cov_sym_t5',
                'prh_ext_cov_sym_t5',
                'vax_status_t5',
                'co_mindset_1_t5':'primals_6_t5',
                'Duration..in.seconds._t6', 'Finished_t6',
                'Step.3.Permission_t6',
                'co_mindset_1_t6':'cmm_4_t6',
                'con_vid_2_q1_t6':'con_vid_2_q2_t6',
                'con_vid_3_q1_t6':'con_vid_3_q2_t6',
                'con_vid_4_q1_t6':'con_vid_4_q2_t6',
                'con_vid_5_q1_t6':'con_vid_5_q2_t6',
                'Duration..in.seconds._t7', 'Finished_t7',
                'COVID.Status_t7',
                'co_mindset_1_t7':'primals_6_t7',
                'Duration..in.seconds._t8', 'Finished_t8',
                "prh_routine_t8",
                  "prh_income_t8",
                "prh_food_t8",
                "prh_housing_t8",
                "prh_medical_t8",
                "prh_mental_t8", 
                "prh_support_t8",
                "prh_stress_t8",
                "prh_discord_t8",
                "prh_care_t8",
                'COVID.Status_t8',
                'COVID.Vaccine.Statu_t8',
                'co_mindset_1_t8':'durability_1_t8',
                'global_wellbeing_1_t8':'sfmm_3_t8',
                'seh_1_1_x_t8', 'seh_1_1_y_t8',
                'seh_2_1_x_t8', 'seh_2_1_y_t8',
                'she_3_1_x_t8', 'she_3_1_y_t8',
                'optimism_1_t8':'primals_6_t8'), as.numeric))

```

## Convert variables into factors or chars as appropriate

```{r}

# Consent

non_physio_merged_raw$consent_pt_1_t5 <- gsub("12", "Agree", non_physio_merged_raw$consent_pt_1_t5)

# Vaccination Status

non_physio_merged_raw$vax_status_t5 <- cut(non_physio_merged_raw$vax_status_t5, 4, labels = c("Fully vaccinated, including booster shot", "Fully vaccinated, not including booster shot", "Partially vaccinated", "Unvaccinated"))

non_physio_merged_raw$COVID.Vaccine.Statu_t8 <- cut(non_physio_merged_raw$COVID.Vaccine.Statu_t8, 3, labels = c("Yes - I got vaccinated for the first time", "Yes - I got an additional COVID-19 vaccine/booster", "No"))

# Religion

non_physio_merged_raw$religion_t5 <- gsub("4", "Jewish", gsub("12", "Christina", gsub("13", "Muslim", 
                                          gsub("14", "Hindu", gsub("15", "Buddhist", gsub("16", "Sikh",
                                          gsub("17", "Baha'i", gsub("18", "Atheist", gsub("19", "Agnostic",
                                          gsub("20", "Other (please specify)", gsub("21", "Nothing in particular",
                                          gsub("22", "Don't know", gsub("23", "Prefer not to say", non_physio_merged_raw$religion_t5)))))))))))))



# Employment, Age, Gender, Race, Income, Marital Status, Political affiliation, 
# Education, Household composition, Caregiving 
# measured at T4 longitudinal for non-physio branch participants




```


## Convert StartDate and EndDate from char to mdy_hm

```{r}

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c("StartDate_t5", "EndDate_t5", "StartDate_t6", "EndDate_t6",
                "StartDate_t7", "EndDate_t7", "StartDate_t8", "EndDate_t8"), 
         mdy_hm))
```

# Change column names to prepare for merging with physio and longitudinal

## Add non-physio branch identifier

```{r}

colnames(non_physio_merged_raw) <- paste(colnames(non_physio_merged_raw), "non_physio", sep = "_")

```


## Additional column name changes as needed

```{r}

non_physio_merged_raw <- non_physio_merged_raw %>% 
  rename("RecipientEmail" = "RecipientEmail_non_physio",
         "religion_non_physio" = "religion_t5_non_physio",
         "phq_1_t5_non_physio" = "phq._1_t5_non_physio",
         "phq_2_t5_non_physio" = "phq._2_t5_non_physio",
         "phq_3_t5_non_physio" = "phq._3_t5_non_physio",
         "phq_4_t5_non_physio" = "phq._4_t5_non_physio",
         "self_efficacy_1_t5_non_physio" = "self.efficacy_1_t5_non_physio",
         "self_efficacy_2_t5_non_physio" = "self.efficacy_2_t5_non_physio",
         "self_efficacy_3_t5_non_physio" = "self.efficacy_3_t5_non_physio",
         "global_health_base_1_t5_non_physio" = "global_health._1_t5_non_physio",
         "global_health_base_2_t5_non_physio" = "global_health._2_t5_non_physio",
         "global_health_base_3_t5_non_physio" = "global_health._3_t5_non_physio",
         "consent_t5_non_physio" = 'consent_pt_1_t5_non_physio',
         "duration_t5_non_physio" = "Duration..in.seconds._t5_non_physio",
         "duration_t6_non_physio" = "Duration..in.seconds._t6_non_physio",
         "duration_t7_non_physio" = "Duration..in.seconds._t7_non_physio",
         "duration_t8_non_physio" = "Duration..in.seconds._t8_non_physio",
         "condition" = "Condition_t6_non_physio",
         "prh_employment_t5_non_physio" = "employment_t5_non_physio",
         "prh_employment_free_t5_non_physio" = "employment_16_TEXT_t5_non_physio",
         "covid_sym_2_free_t5_non_physio" = "covid_sym_2_29_TEXT_t5_non_physio",
         "religion_free_t5_non_physio" = "religion_20_TEXT_t5_non_physio",
         "cov_sym_t7_non_physio" = "COVID.Symptoms_t7_non_physio",
         "cov_sym_free_t7_non_physio" = "COVID.Symptoms_29_TEXT_t7_non_physio",
         "cov_sym_t8_non_physio" = "COVID.Symptoms_t8_non_physio",
         "cov_sym_free_t8_non_physio" = "COVID.Symptoms_29_TEXT_t8_non_physio",
         "extraversion_t8_non_physio" = "personality_1_t8_non_physio",
         "openness_t8_non_physio" = "personality_2_t8_non_physio",
         "stability_t8_non_physio" = "personality_3_t8_non_physio",
         "warmness_t8_non_physio" = 'personality_4_t8_non_physio',
         "dependability_t8_non_physio" = "personality_5_t8_non_physio",
         "seh_3_1_x_t8_non_physio" = "she_3_1_x_t8_non_physio",
         "seh_3_1_y_t8_non_physio" = "she_3_1_y_t8_non_physio",
         "seh_3_t8_non_physio" = "she_3_t8_non_physio",
         "participant_id" = "participant_id_non_physio"
         )

```


# Participant retention

## Calculate dropout time

```{r}
# Change all Finished_tX_non_physio to factor variables:

## T5

non_physio_merged_raw$Finished_t5_non_physio <- as.factor(non_physio_merged_raw$Finished_t5_non_physio)

## T6

non_physio_merged_raw$Finished_t6_non_physio <- as.factor(non_physio_merged_raw$Finished_t6_non_physio)

## T7

non_physio_merged_raw$Finished_t7_non_physio <- as.factor(non_physio_merged_raw$Finished_t7_non_physio)

## T8

non_physio_merged_raw$Finished_t8_non_physio <- as.factor(non_physio_merged_raw$Finished_t8_non_physio)

# Replace NA with '0' for all Finished_tX_non_physio variables:

## T5 - Not needed (all participants completed T5 survey)

## T6

non_physio_merged_raw$Finished_t6_non_physio[is.na(non_physio_merged_raw$Finished_t6_non_physio)] <- 0

## T7

non_physio_merged_raw$Finished_t7_non_physio[is.na(non_physio_merged_raw$Finished_t7_non_physio)] <- 0

## T8

non_physio_merged_raw$Finished_t8_non_physio[is.na(non_physio_merged_raw$Finished_t8_non_physio)] <- 0

# Create a retention variable of progression through study surveys. Showing when participants were lost to follow-up, and when participants did not complete (DNC) a timepoint but did return to the study for a later timepoint.
## Note: T5 not included as all participants completed T5 survey.

non_physio_merged_raw <- non_physio_merged_raw %>%
mutate(participant_retention_non_physio = case_when(Finished_t8_non_physio == '1' & Finished_t7_non_physio == '1' &    Finished_t6_non_physio == '1'  ~ "All", #Completed ALL timepoints
                                                    Finished_t8_non_physio == '0' & Finished_t7_non_physio == '1' & Finished_t6_non_physio == '0' ~ "N/T6, Y/T7, N/T8", #DNC T6, returned for T7, lost at T8
                                                    Finished_t8_non_physio == '1' & Finished_t7_non_physio == '0' & Finished_t6_non_physio == '1' ~ "Y/T6, N/T7, Y/T8", #DNC T7, returned for T8
                                                    Finished_t8_non_physio == '1' & Finished_t7_non_physio == '0' & Finished_t6_non_physio == '0' ~ "N/T6/T7, Y/T8", #DNC T6 or T7, returned for T8
                                                    Finished_t8_non_physio == '1' & Finished_t7_non_physio == '1' & Finished_t6_non_physio == '0' ~ "N/T6, Y/T7/T8", #DNC T6, returned for T7 & T8
                                                    Finished_t8_non_physio == '0' & Finished_t7_non_physio == '1' & Finished_t6_non_physio == '1' ~ "T8", #Lost at T8
                                                    Finished_t8_non_physio == '0' & Finished_t7_non_physio == '0' & Finished_t6_non_physio == '1' ~ "T7", #Lost at T7
                                                    Finished_t8_non_physio == '0' & Finished_t7_non_physio == '0' & Finished_t6_non_physio == '0' ~ "T6" )) #Lost at T6

```

## Calculate intervention/control completion

```{r}

# Add intervention/control column to non_physio_merged_raw

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(int_con_completion_non_physio = case_when(Finished_t6_non_physio == "1" ~ "Complete",
                                                   Finished_t6_non_physio != "1" ~ "Incomplete"))

```



# Calculate summary scores

## PTGI full

### Reverse score and rescale items

```{r}

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(ptg_1_t5_non_physio:ptg_21_t5_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(ptg_1_t7_non_physio:ptg_21_t7_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(ptg_1_t8_non_physio:ptg_21_t8_non_physio), ~.-1))

```

### Calculate summary scores and alphas

```{r}

# Calculate summary scores

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_full_t5_non_physio = rowSums(select(., ptg_1_t5_non_physio:ptg_21_t5_non_physio)))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_full_t7_non_physio = rowSums(select(., ptg_1_t7_non_physio:ptg_21_t7_non_physio)))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_full_t8_non_physio = rowSums(select(., ptg_1_t8_non_physio:ptg_21_t8_non_physio)))

# Make summary score dataframes and calculate alphas

ptgi_full_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t5_non_physio:ptg_21_t5_non_physio)

psych::alpha(ptgi_full_t5_non_physio_df)

ptgi_full_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t7_non_physio:ptg_21_t7_non_physio)

psych::alpha(ptgi_full_t7_non_physio_df)

ptgi_full_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t8_non_physio:ptg_21_t8_non_physio)

psych::alpha(ptgi_full_t8_non_physio_df)


```

## PTGI abridged

### Calculate summary scores and alphas

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_abridged_t5_non_physio = (ptg_1_t5_non_physio + ptg_2_t5_non_physio + ptg_3_t5_non_physio + ptg_4_t5_non_physio + ptg_6_t5_non_physio + ptg_7_t5_non_physio + ptg_8_t5_non_physio + ptg_9_t5_non_physio + ptg_10_t5_non_physio + ptg_11_t5_non_physio + ptg_12_t5_non_physio + ptg_13_t5_non_physio + ptg_14_t5_non_physio + ptg_15_t5_non_physio + ptg_16_t5_non_physio + ptg_17_t5_non_physio + ptg_18_t5_non_physio + ptg_20_t5_non_physio + ptg_21_t5_non_physio))


ptgi_abridged_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t5_non_physio, ptg_2_t5_non_physio, ptg_3_t5_non_physio, ptg_4_t5_non_physio, ptg_6_t5_non_physio, ptg_7_t5_non_physio, ptg_8_t5_non_physio, ptg_9_t5_non_physio, ptg_10_t5_non_physio, ptg_11_t5_non_physio, ptg_12_t5_non_physio, ptg_13_t5_non_physio, ptg_14_t5_non_physio, ptg_15_t5_non_physio, ptg_16_t5_non_physio, ptg_17_t5_non_physio, ptg_18_t5_non_physio, ptg_20_t5_non_physio, ptg_21_t5_non_physio)

psych::alpha(ptgi_abridged_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_abridged_t7_non_physio = (ptg_1_t7_non_physio + ptg_2_t7_non_physio + ptg_3_t7_non_physio + ptg_4_t7_non_physio + ptg_6_t7_non_physio + ptg_7_t7_non_physio + ptg_8_t7_non_physio + ptg_9_t7_non_physio + ptg_10_t7_non_physio + ptg_11_t7_non_physio + ptg_12_t7_non_physio + ptg_13_t7_non_physio + ptg_14_t7_non_physio + ptg_15_t7_non_physio + ptg_16_t7_non_physio + ptg_17_t7_non_physio + ptg_18_t7_non_physio + ptg_20_t7_non_physio + ptg_21_t7_non_physio))


ptgi_abridged_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t7_non_physio, ptg_2_t7_non_physio, ptg_3_t7_non_physio, ptg_4_t7_non_physio, ptg_6_t7_non_physio, ptg_7_t7_non_physio, ptg_8_t7_non_physio, ptg_9_t7_non_physio, ptg_10_t7_non_physio, ptg_11_t7_non_physio,
         ptg_12_t7_non_physio, ptg_13_t7_non_physio, ptg_14_t7_non_physio, ptg_15_t7_non_physio, ptg_16_t7_non_physio, ptg_17_t7_non_physio, ptg_18_t7_non_physio, ptg_20_t7_non_physio, ptg_21_t7_non_physio)

psych::alpha(ptgi_abridged_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_abridged_t8_non_physio = (ptg_1_t8_non_physio + ptg_2_t8_non_physio + ptg_3_t8_non_physio + ptg_4_t8_non_physio + ptg_6_t8_non_physio + ptg_7_t8_non_physio + ptg_8_t8_non_physio + ptg_9_t8_non_physio + ptg_10_t8_non_physio + ptg_11_t8_non_physio + ptg_12_t8_non_physio + ptg_13_t8_non_physio + ptg_14_t8_non_physio + ptg_15_t8_non_physio + ptg_16_t8_non_physio + ptg_17_t8_non_physio + ptg_18_t8_non_physio + ptg_20_t8_non_physio + ptg_21_t8_non_physio))


ptgi_abridged_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(ptg_1_t8_non_physio, ptg_2_t8_non_physio, ptg_3_t8_non_physio, ptg_4_t8_non_physio, ptg_6_t8_non_physio, ptg_7_t8_non_physio, ptg_8_t8_non_physio, ptg_9_t8_non_physio, ptg_10_t8_non_physio, ptg_11_t8_non_physio,
         ptg_12_t8_non_physio, ptg_13_t8_non_physio, ptg_14_t8_non_physio, ptg_15_t8_non_physio, ptg_16_t8_non_physio, ptg_17_t8_non_physio, ptg_18_t8_non_physio, ptg_20_t8_non_physio, ptg_21_t8_non_physio)

psych::alpha(ptgi_abridged_t8_non_physio_df)

```

## PTGI subscales

### Calculate summary scores

```{r}

# T5

## Relationships 

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_relationships_t5_non_physio = (ptg_6_t5_non_physio + ptg_7_t5_non_physio + 
                                    ptg_9_t5_non_physio + ptg_12_t5_non_physio + ptg_15_t5_non_physio + ptg_17_t5_non_physio + ptg_20_t5_non_physio))

ptgi_relationships_t5_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_6_t5_non_physio, ptg_7_t5_non_physio, 
                                    ptg_9_t5_non_physio, ptg_12_t5_non_physio, ptg_15_t5_non_physio, ptg_17_t5_non_physio, ptg_20_t5_non_physio)

psych::alpha(ptgi_relationships_t5_df_non_physio)

## Possibilities

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_possibilities_t5_non_physio = (ptg_2_t5_non_physio + ptg_13_t5_non_physio + 
        ptg_14_t5_non_physio + ptg_18_t5_non_physio + ptg_21_t5_non_physio))

ptgi_possibilities_t5_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_2_t5_non_physio, ptg_13_t5_non_physio, 
        ptg_14_t5_non_physio, ptg_18_t5_non_physio, ptg_21_t5_non_physio)

psych::alpha(ptgi_possibilities_t5_df_non_physio)

## Strength

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_strength_t5_non_physio = (ptg_4_t5_non_physio + ptg_8_t5_non_physio + 
        ptg_10_t5_non_physio + ptg_16_t5_non_physio))

ptgi_strength_t5_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_4_t5_non_physio, ptg_8_t5_non_physio,  
        ptg_10_t5_non_physio, ptg_16_t5_non_physio)

psych::alpha(ptgi_strength_t5_df_non_physio)

## Appreciation

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_appreciation_t5_non_physio = (ptg_1_t5_non_physio + ptg_3_t5_non_physio + 
        ptg_11_t5_non_physio))

ptgi_appreciation_t5_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_1_t5_non_physio, ptg_3_t5_non_physio,  
        ptg_11_t5_non_physio)

psych::alpha(ptgi_appreciation_t5_df_non_physio)

## Spiritual

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_spiritual_t5_non_physio = (ptg_5_t5_non_physio + ptg_19_t5_non_physio))

ptgi_spiritual_t5_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_5_t5_non_physio, ptg_19_t5_non_physio)

psych::alpha(ptgi_spiritual_t5_df_non_physio)


# T7

## Relationships 

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_relationships_t7_non_physio = (ptg_6_t7_non_physio + ptg_7_t7_non_physio + 
                                    ptg_9_t7_non_physio + ptg_12_t7_non_physio + ptg_15_t7_non_physio + ptg_17_t7_non_physio + ptg_20_t7_non_physio))

ptgi_relationships_t7_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_6_t7_non_physio, ptg_7_t7_non_physio, 
                                    ptg_9_t7_non_physio, ptg_12_t7_non_physio, ptg_15_t7_non_physio, ptg_17_t7_non_physio, ptg_20_t7_non_physio)

psych::alpha(ptgi_relationships_t7_df_non_physio)

## Possibilities

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_possibilities_t7_non_physio = (ptg_2_t7_non_physio + ptg_13_t7_non_physio + 
        ptg_14_t7_non_physio + ptg_18_t7_non_physio + ptg_21_t7_non_physio))

ptgi_possibilities_t7_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_2_t7_non_physio, ptg_13_t7_non_physio, 
        ptg_14_t7_non_physio, ptg_18_t7_non_physio, ptg_21_t7_non_physio)

psych::alpha(ptgi_possibilities_t7_df_non_physio)

## Strength

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_strength_t7_non_physio = (ptg_4_t7_non_physio + ptg_8_t7_non_physio + 
        ptg_10_t7_non_physio + ptg_16_t7_non_physio))

ptgi_strength_t7_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_4_t7_non_physio, ptg_8_t7_non_physio,  
        ptg_10_t7_non_physio, ptg_16_t7_non_physio)

psych::alpha(ptgi_strength_t7_df_non_physio)

## Appreciation

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_appreciation_t7_non_physio = (ptg_1_t7_non_physio + ptg_3_t7_non_physio + 
        ptg_11_t7_non_physio))

ptgi_appreciation_t7_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_1_t7_non_physio, ptg_3_t7_non_physio,  
        ptg_11_t7_non_physio)

psych::alpha(ptgi_appreciation_t7_df_non_physio)

## Spiritual

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_spiritual_t7_non_physio = (ptg_5_t7_non_physio + ptg_19_t7_non_physio))

ptgi_spiritual_t7_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_5_t7_non_physio, ptg_19_t7_non_physio)

psych::alpha(ptgi_spiritual_t7_df_non_physio)

# T8

## Relationships 

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_relationships_t8_non_physio = (ptg_6_t8_non_physio + ptg_7_t8_non_physio + 
                                    ptg_9_t8_non_physio + ptg_12_t8_non_physio + ptg_15_t8_non_physio + ptg_17_t8_non_physio + ptg_20_t8_non_physio))

ptgi_relationships_t8_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_6_t8_non_physio, ptg_7_t8_non_physio, 
                                    ptg_9_t8_non_physio, ptg_12_t8_non_physio, ptg_15_t8_non_physio, ptg_17_t8_non_physio, ptg_20_t8_non_physio)

psych::alpha(ptgi_relationships_t8_df_non_physio)

## Possibilities

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_possibilities_t8_non_physio = (ptg_2_t8_non_physio + ptg_13_t8_non_physio + 
        ptg_14_t8_non_physio + ptg_18_t8_non_physio + ptg_21_t8_non_physio))

ptgi_possibilities_t8_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_2_t8_non_physio, ptg_13_t8_non_physio, 
        ptg_14_t8_non_physio, ptg_18_t8_non_physio, ptg_21_t8_non_physio)

psych::alpha(ptgi_possibilities_t8_df_non_physio)

## Strength

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_strength_t8_non_physio = (ptg_4_t8_non_physio + ptg_8_t8_non_physio + 
        ptg_10_t8_non_physio + ptg_16_t8_non_physio))

ptgi_strength_t8_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_4_t8_non_physio, ptg_8_t8_non_physio,  
        ptg_10_t8_non_physio, ptg_16_t8_non_physio)

psych::alpha(ptgi_strength_t8_df_non_physio)

## Appreciation

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_appreciation_t8_non_physio = (ptg_1_t8_non_physio + ptg_3_t8_non_physio + 
        ptg_11_t8_non_physio))

ptgi_appreciation_t8_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_1_t8_non_physio, ptg_3_t8_non_physio,  
        ptg_11_t8_non_physio)

psych::alpha(ptgi_appreciation_t8_df_non_physio)

## Spiritual

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(ptgi_spiritual_t8_non_physio = (ptg_5_t8_non_physio + ptg_19_t8_non_physio))

ptgi_spiritual_t8_df_non_physio <- non_physio_merged_raw %>% 
  select(ptg_5_t8_non_physio, ptg_19_t8_non_physio)

psych::alpha(ptgi_spiritual_t8_df_non_physio)


```


# CO Mindset

## Reverse score items 

```{r}

#T5 Reverse Scoring 

co_reverse_columns_t5 <- non_physio_merged_raw %>% 
  select(co_mindset_1_t5_non_physio, co_mindset_3_t5_non_physio, co_mindset_4_t5_non_physio,
         co_mindset_7_t5_non_physio, co_mindset_9_t5_non_physio) %>% 
  colnames()


non_physio_merged_raw[ ,co_reverse_columns_t5] <- 8 - non_physio_merged_raw[ ,co_reverse_columns_t5]

# T6

co_reverse_columns_t6 <- non_physio_merged_raw %>% 
  select(co_mindset_1_t6_non_physio, co_mindset_3_t6_non_physio, co_mindset_4_t6_non_physio,
         co_mindset_7_t6_non_physio, co_mindset_9_t6_non_physio) %>% 
  colnames()


non_physio_merged_raw[ ,co_reverse_columns_t6] <- 8 - non_physio_merged_raw[ ,co_reverse_columns_t6]

#T7 Reverse Scoring 

co_reverse_columns_t7 <- non_physio_merged_raw %>% 
  select(co_mindset_1_t7_non_physio, co_mindset_3_t7_non_physio, co_mindset_4_t7_non_physio,
         co_mindset_7_t7_non_physio, co_mindset_9_t7_non_physio) %>% 
  colnames()


non_physio_merged_raw[ ,co_reverse_columns_t7] <- 8 - non_physio_merged_raw[ ,co_reverse_columns_t7]

#T8 Reverse Scoring 

co_reverse_columns_t8 <- non_physio_merged_raw %>% 
  select(co_mindset_1_t8_non_physio, co_mindset_3_t8_non_physio, co_mindset_4_t8_non_physio,
         co_mindset_7_t8_non_physio, co_mindset_9_t8_non_physio) %>% 
  colnames()


non_physio_merged_raw[ ,co_reverse_columns_t8] <- 8 - non_physio_merged_raw[ ,co_reverse_columns_t8]


```

## Calculate summary scores and alphas CO Mindset 

```{r calculate summary scores for comindset}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(co_mindset_t5_non_physio = rowMeans(select(., co_mindset_1_t5_non_physio:co_mindset_10_t5_non_physio)))

co_mindset_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(co_mindset_1_t5_non_physio:co_mindset_10_t5_non_physio)

psych::alpha(co_mindset_t5_non_physio_df)


# T6

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(co_mindset_t6_non_physio = rowMeans(select(., co_mindset_1_t6_non_physio:co_mindset_10_t6_non_physio)))

co_mindset_t6_non_physio_df <- non_physio_merged_raw %>% 
  select(co_mindset_1_t6_non_physio:co_mindset_10_t6_non_physio)

psych::alpha(co_mindset_t6_non_physio_df)



# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(co_mindset_t7_non_physio = rowMeans(select(., co_mindset_1_t7_non_physio:co_mindset_10_t7_non_physio)))

co_mindset_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(co_mindset_1_t7_non_physio:co_mindset_10_t7_non_physio)

psych::alpha(co_mindset_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(co_mindset_t8_non_physio = rowMeans(select(., co_mindset_1_t8_non_physio:co_mindset_10_t8_non_physio)))

co_mindset_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(co_mindset_1_t8_non_physio:co_mindset_10_t8_non_physio)

psych::alpha(co_mindset_t8_non_physio_df)

```

## Positive Affect

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(pos_affect_t5_non_physio = rowSums(select(., panas_1_t5_non_physio, panas_3_t5_non_physio , panas_5_t5_non_physio, panas_9_t5_non_physio, panas_10_t5_non_physio, panas_12_t5_non_physio,  panas_14_t5_non_physio, panas_16_t5_non_physio, panas_17_t5_non_physio, panas_19_t5_non_physio)))

pos_affect_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_1_t5_non_physio, panas_3_t5_non_physio , panas_5_t5_non_physio, panas_9_t5_non_physio, panas_10_t5_non_physio, panas_12_t5_non_physio,  panas_14_t5_non_physio, panas_16_t5_non_physio, panas_17_t5_non_physio, panas_19_t5_non_physio)

psych::alpha(pos_affect_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(pos_affect_t7_non_physio = rowSums(select(., panas_1_t7_non_physio, panas_3_t7_non_physio , panas_5_t7_non_physio, panas_9_t7_non_physio, panas_10_t7_non_physio, panas_12_t7_non_physio,  panas_14_t7_non_physio, panas_16_t7_non_physio, panas_17_t7_non_physio, panas_19_t7_non_physio)))

pos_affect_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_1_t7_non_physio, panas_3_t7_non_physio , panas_5_t7_non_physio, panas_9_t7_non_physio, panas_10_t7_non_physio, panas_12_t7_non_physio,  panas_14_t7_non_physio, panas_16_t7_non_physio, panas_17_t7_non_physio, panas_19_t7_non_physio)

psych::alpha(pos_affect_t7_non_physio_df)


# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(pos_affect_t8_non_physio = rowSums(select(., panas_1_t8_non_physio, panas_3_t8_non_physio , panas_5_t8_non_physio, panas_9_t8_non_physio, panas_10_t8_non_physio, panas_12_t8_non_physio,  panas_14_t8_non_physio, panas_16_t8_non_physio, panas_17_t8_non_physio, panas_19_t8_non_physio)))

pos_affect_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_1_t8_non_physio, panas_3_t8_non_physio , panas_5_t8_non_physio, panas_9_t8_non_physio, panas_10_t8_non_physio, panas_12_t8_non_physio,  panas_14_t8_non_physio, panas_16_t8_non_physio, panas_17_t8_non_physio, panas_19_t8_non_physio)

psych::alpha(pos_affect_t8_non_physio_df)


```


## Negative Affect

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(neg_affect_t5_non_physio = rowSums(select(., panas_2_t5_non_physio, panas_4_t5_non_physio , panas_6_t5_non_physio, panas_7_t5_non_physio, panas_8_t5_non_physio, panas_11_t5_non_physio,  panas_13_t5_non_physio, panas_15_t5_non_physio, panas_18_t5_non_physio, panas_20_t5_non_physio)))

neg_affect_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_2_t5_non_physio, panas_4_t5_non_physio , panas_6_t5_non_physio, panas_7_t5_non_physio, panas_8_t5_non_physio, panas_11_t5_non_physio,  panas_13_t5_non_physio, panas_15_t5_non_physio, panas_18_t5_non_physio, panas_20_t5_non_physio)

psych::alpha(neg_affect_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(neg_affect_t7_non_physio = rowSums(select(., panas_2_t7_non_physio, panas_4_t7_non_physio , panas_6_t7_non_physio, panas_7_t7_non_physio, panas_8_t7_non_physio, panas_11_t7_non_physio,  panas_13_t7_non_physio, panas_15_t7_non_physio, panas_18_t7_non_physio, panas_20_t7_non_physio)))

neg_affect_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_2_t7_non_physio, panas_4_t7_non_physio , panas_6_t7_non_physio, panas_7_t7_non_physio, panas_8_t7_non_physio, panas_11_t7_non_physio,  panas_13_t7_non_physio, panas_15_t7_non_physio, panas_18_t7_non_physio, panas_20_t7_non_physio)

psych::alpha(neg_affect_t7_non_physio_df)


# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(neg_affect_t8_non_physio = rowSums(select(., panas_2_t8_non_physio, panas_4_t8_non_physio , panas_6_t8_non_physio, panas_7_t8_non_physio, panas_8_t8_non_physio, panas_11_t8_non_physio,  panas_13_t8_non_physio, panas_15_t8_non_physio, panas_18_t8_non_physio, panas_20_t8_non_physio)))

neg_affect_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(panas_2_t8_non_physio, panas_4_t8_non_physio , panas_6_t8_non_physio, panas_7_t8_non_physio, panas_8_t8_non_physio, panas_11_t8_non_physio,  panas_13_t8_non_physio, panas_15_t8_non_physio, panas_18_t8_non_physio, panas_20_t8_non_physio)

psych::alpha(neg_affect_t8_non_physio_df)


```

## PHQ-4

### Rescale items

```{r}

# Rescale from a 1-4 to a 0-3 scale

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(phq_1_t5_non_physio:phq_4_t5_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(phq_1_t7_non_physio:phq_4_t7_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(phq_1_t8_non_physio:phq_4_t8_non_physio), ~.-1))


```

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_full_t5_non_physio = rowSums(select(., phq_1_t5_non_physio:phq_4_t5_non_physio)))

phq_full_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t5_non_physio:phq_4_t5_non_physio)

psych::alpha(phq_full_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_full_t7_non_physio = rowSums(select(., phq_1_t7_non_physio:phq_4_t7_non_physio)))

phq_full_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t7_non_physio:phq_4_t7_non_physio)

psych::alpha(phq_full_t7_non_physio_df)


# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_full_t8_non_physio = rowSums(select(., phq_1_t8_non_physio:phq_4_t8_non_physio)))

phq_full_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t8_non_physio:phq_4_t8_non_physio)

psych::alpha(phq_full_t8_non_physio_df)

```

## PHQ - Anxiety

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_anxiety_t5_non_physio = rowSums(select(., phq_1_t5_non_physio:phq_2_t5_non_physio)))

phq_anxiety_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t5_non_physio:phq_2_t5_non_physio)

psych::alpha(phq_anxiety_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_anxiety_t7_non_physio = rowSums(select(., phq_1_t7_non_physio:phq_2_t7_non_physio)))

phq_anxiety_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t7_non_physio:phq_2_t7_non_physio)

psych::alpha(phq_anxiety_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_anxiety_t8_non_physio = rowSums(select(., phq_1_t8_non_physio:phq_2_t8_non_physio)))

phq_anxiety_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_1_t8_non_physio:phq_2_t8_non_physio)

psych::alpha(phq_anxiety_t8_non_physio_df)

```

## PHQ - Depression

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_depression_t5_non_physio = rowSums(select(., phq_3_t5_non_physio:phq_4_t5_non_physio)))

phq_depression_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_3_t5_non_physio:phq_4_t5_non_physio)

psych::alpha(phq_depression_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_depression_t7_non_physio = rowSums(select(., phq_3_t7_non_physio:phq_4_t7_non_physio)))

phq_depression_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_3_t7_non_physio:phq_4_t7_non_physio)

psych::alpha(phq_depression_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(phq_depression_t8_non_physio = rowSums(select(., phq_3_t8_non_physio:phq_4_t8_non_physio)))

phq_depression_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(phq_3_t8_non_physio:phq_4_t8_non_physio)

psych::alpha(phq_depression_t8_non_physio_df)

```


## Global Health - Combined (Physical, Mental, QoL)

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(global_health_full_t5_non_physio = rowMeans(select(., global_health_base_1_t5_non_physio:global_health_base_3_t5_non_physio)))

global_health_full_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(global_health_base_1_t5_non_physio:global_health_base_3_t5_non_physio)

psych::alpha(global_health_full_t5_non_physio_df)


# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(global_health_full_t7_non_physio = rowMeans(select(., global_wellbeing_1_t7_non_physio:global_wellbeing_3_t7_non_physio)))

global_health_full_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(global_wellbeing_1_t7_non_physio:global_wellbeing_3_t7_non_physio)

psych::alpha(global_health_full_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(global_health_full_t8_non_physio = rowMeans(select(., global_wellbeing_1_t8_non_physio:global_wellbeing_3_t8_non_physio)))

global_health_full_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(global_wellbeing_1_t8_non_physio:global_wellbeing_3_t8_non_physio)

psych::alpha(global_health_full_t8_non_physio_df)

```


## Social Well-Being (MHC-SF Social Well-Being subscale)

### Rescale items

```{r}

# Rescale items from a 1-6 to a 0-5 scale

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(social_wellbeing_1_t5_non_physio:social_wellbeing_5_t5_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(social_wellbeing_1_t7_non_physio:social_wellbeing_5_t7_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(social_wellbeing_1_t8_non_physio:social_wellbeing_5_t8_non_physio), ~.-1))

```

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(swb_t5_non_physio = rowSums(select(., social_wellbeing_1_t5_non_physio:social_wellbeing_5_t5_non_physio)))

swb_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(social_wellbeing_1_t5_non_physio:social_wellbeing_5_t5_non_physio)

psych::alpha(swb_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(swb_t7_non_physio = rowSums(select(., social_wellbeing_1_t7_non_physio:social_wellbeing_5_t7_non_physio)))

swb_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(social_wellbeing_1_t7_non_physio:social_wellbeing_5_t7_non_physio)

psych::alpha(swb_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(swb_t8_non_physio = rowSums(select(., social_wellbeing_1_t8_non_physio:social_wellbeing_5_t8_non_physio)))

swb_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(social_wellbeing_1_t8_non_physio:social_wellbeing_5_t8_non_physio)

psych::alpha(swb_t8_non_physio_df)


```


## Meaning - Presence Subscale

### Reverse score items

```{r}

non_physio_merged_raw[ ,"meaning_6_t5_non_physio"] <- 8 - non_physio_merged_raw[ ,"meaning_6_t5_non_physio"]

non_physio_merged_raw[ ,"meaning_6_t7_non_physio"] <- 8 - non_physio_merged_raw[ ,"meaning_6_t7_non_physio"]

non_physio_merged_raw[ ,"meaning_6_t8_non_physio"] <- 8 - non_physio_merged_raw[ ,"meaning_6_t8_non_physio"]

```

### Calculate summary scores and alphas

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_presence_t5_non_physio = rowSums(select(., meaning_1_t5_non_physio, meaning_4_t5_non_physio:meaning_6_t5_non_physio)))

meaning_presence_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_1_t5_non_physio, meaning_4_t5_non_physio:meaning_6_t5_non_physio)

psych::alpha(meaning_presence_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_presence_t7_non_physio = rowSums(select(., meaning_1_t7_non_physio, meaning_4_t7_non_physio:meaning_6_t7_non_physio)))

meaning_presence_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_1_t7_non_physio, meaning_4_t7_non_physio:meaning_6_t7_non_physio)

psych::alpha(meaning_presence_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_presence_t8_non_physio = rowSums(select(., meaning_1_t8_non_physio, meaning_4_t8_non_physio:meaning_6_t8_non_physio)))

meaning_presence_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_1_t8_non_physio, meaning_4_t8_non_physio:meaning_6_t8_non_physio)

psych::alpha(meaning_presence_t8_non_physio_df)



```

## Meaning - Search subscale

### Calculate summary scores and alphas

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_search_t5_non_physio = rowSums(select(., meaning_2_t5_non_physio, meaning_3_t5_non_physio)))

meaning_search_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_2_t5_non_physio, meaning_3_t5_non_physio)

psych::alpha(meaning_search_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_search_t7_non_physio = rowSums(select(., meaning_2_t7_non_physio, meaning_3_t7_non_physio)))

meaning_search_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_2_t7_non_physio, meaning_3_t7_non_physio)

psych::alpha(meaning_search_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(meaning_search_t8_non_physio = rowSums(select(., meaning_2_t8_non_physio, meaning_3_t8_non_physio)))

meaning_search_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(meaning_2_t8_non_physio, meaning_3_t8_non_physio)

psych::alpha(meaning_search_t8_non_physio_df)


```

## Resilience

### Reverse score items

```{r}

# T5

non_physio_merged_raw[ ,"resilience_2_t5_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_2_t5_non_physio"]

non_physio_merged_raw[ ,"resilience_3_t5_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_3_t5_non_physio"]

# T7

non_physio_merged_raw[ ,"resilience_2_t7_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_2_t7_non_physio"]

non_physio_merged_raw[ ,"resilience_3_t7_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_3_t7_non_physio"]

# T8

non_physio_merged_raw[ ,"resilience_2_t8_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_2_t8_non_physio"]

non_physio_merged_raw[ ,"resilience_3_t8_non_physio"] <- 6 - non_physio_merged_raw[ ,"resilience_3_t8_non_physio"]


```

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(resilience_t5_non_physio = rowMeans(select(.,resilience_1_t5_non_physio:resilience_4_t5_non_physio)))

resilience_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(resilience_1_t5_non_physio:resilience_4_t5_non_physio)

psych::alpha(resilience_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(resilience_t7_non_physio = rowMeans(select(.,resilience_1_t7_non_physio:resilience_4_t7_non_physio)))

resilience_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(resilience_1_t7_non_physio:resilience_4_t7_non_physio)

psych::alpha(resilience_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(resilience_t8_non_physio = rowMeans(select(.,resilience_1_t8_non_physio:resilience_4_t8_non_physio)))

resilience_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(resilience_1_t8_non_physio:resilience_4_t8_non_physio)

psych::alpha(resilience_t8_non_physio_df)


```

## Closeness

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(closeness_t5_non_physio = rowSums(select(.,closeness_1_t5_non_physio:closeness_4_t5_non_physio)))

closeness_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(closeness_1_t5_non_physio:closeness_4_t5_non_physio)

psych::alpha(closeness_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(closeness_t7_non_physio = rowSums(select(.,closeness_1_t7_non_physio:closeness_4_t7_non_physio)))

closeness_t7_non_physio_df <- non_physio_merged_raw %>% 
  select(closeness_1_t7_non_physio:closeness_4_t7_non_physio)

psych::alpha(closeness_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(closeness_t8_non_physio = rowSums(select(.,closeness_1_t8_non_physio:closeness_4_t8_non_physio)))

closeness_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(closeness_1_t8_non_physio:closeness_4_t8_non_physio)

psych::alpha(closeness_t8_non_physio_df)


```

## Cognitive Flexibility

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(cog_flexibility_t5_non_physio = rowMeans(select(.,cog_flexibility_1_t5_non_physio:cog_flexibility_12_t5_non_physio)))

cog_flexibility_t5_non_physio_df <- non_physio_merged_raw %>%
  select(cog_flexibility_1_t5_non_physio:cog_flexibility_12_t5_non_physio)

psych::alpha(cog_flexibility_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(cog_flexibility_t7_non_physio = rowMeans(select(.,cog_flexibility_1_t7_non_physio:cog_flexibility_12_t7_non_physio)))

cog_flexibility_t7_non_physio_df <- non_physio_merged_raw %>%
  select(cog_flexibility_1_t7_non_physio:cog_flexibility_12_t7_non_physio)

psych::alpha(cog_flexibility_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(cog_flexibility_t8_non_physio = rowMeans(select(.,cog_flexibility_1_t8_non_physio:cog_flexibility_12_t8_non_physio)))

cog_flexibility_t8_non_physio_df <- non_physio_merged_raw %>%
  select(cog_flexibility_1_t8_non_physio:cog_flexibility_12_t8_non_physio)

psych::alpha(cog_flexibility_t8_non_physio_df)

```

## Primal World-Beliefs

### Rescale items

```{r}

# Rescale items from a 1-6 to a 0-5 scale

# T5

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(across(c(primals_1_t5_non_physio:primals_6_t5_non_physio), ~.-1))

# T7

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(across(c(primals_1_t7_non_physio:primals_6_t7_non_physio), ~.-1))

# T8

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(across(c(primals_1_t8_non_physio:primals_6_t8_non_physio), ~.-1))

```

### Reverse score items

```{r}

# Reverse score questions 3, 4, and 6

# T5

non_physio_merged_raw[ ,'primals_3_t5_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_3_t5_non_physio']
non_physio_merged_raw[ ,'primals_4_t5_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_4_t5_non_physio']
non_physio_merged_raw[ ,'primals_6_t5_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_6_t5_non_physio']

# T7

non_physio_merged_raw[ ,'primals_3_t7_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_3_t7_non_physio']
non_physio_merged_raw[ ,'primals_4_t7_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_4_t7_non_physio']
non_physio_merged_raw[ ,'primals_6_t7_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_6_t7_non_physio']

#T8

non_physio_merged_raw[ ,'primals_3_t8_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_3_t8_non_physio']
non_physio_merged_raw[ ,'primals_4_t8_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_4_t8_non_physio']
non_physio_merged_raw[ ,'primals_6_t8_non_physio'] <- 5 - non_physio_merged_raw[ ,'primals_6_t8_non_physio']

```

### Calculate summary scores

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(primals_t5_non_physio = rowMeans(select(.,primals_1_t5_non_physio:primals_6_t5_non_physio)))

primals_t5_non_physio_df <- non_physio_merged_raw %>%
  select(primals_1_t5_non_physio:primals_6_t5_non_physio)

psych::alpha(primals_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(primals_t7_non_physio = rowMeans(select(.,primals_1_t7_non_physio:primals_6_t7_non_physio)))

primals_t7_non_physio_df <- non_physio_merged_raw %>%
  select(primals_1_t7_non_physio:primals_6_t7_non_physio)

psych::alpha(primals_t7_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(primals_t8_non_physio = rowMeans(select(.,primals_1_t8_non_physio:primals_6_t8_non_physio)))

primals_t8_non_physio_df <- non_physio_merged_raw %>%
  select(primals_1_t8_non_physio:primals_6_t8_non_physio)

psych::alpha(primals_t8_non_physio_df)

```


### Rescale items SFMM

```{r}

# Rescale items from a 1-6 to a 0-5 scale

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(sfmm_1_t5_non_physio:sfmm_3_t5_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(sfmm_1_t7_non_physio:sfmm_3_t7_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(sfmm_1_t8_non_physio:sfmm_3_t8_non_physio), ~.-1))


```


### Calculate summary scores SFMM

```{r}

# T5

non_physio_merged_raw  <- non_physio_merged_raw  %>% 
  mutate(sfmm_t5_non_physio = rowMeans(select(., sfmm_1_t5_non_physio:sfmm_3_t5_non_physio)))

sfmm_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(sfmm_1_t5_non_physio:sfmm_3_t5_non_physio)

psych::alpha(sfmm_t5_non_physio_df)

# T7

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(sfmm_t7_non_physio = rowMeans(select(., sfmm_1_t7_non_physio:sfmm_3_t7_non_physio)))

sfmm_t7_non_physio_df <- non_physio_merged_raw %>%
  select(sfmm_1_t7_non_physio:sfmm_3_t7_non_physio)

psych::alpha(sfmm_t7_non_physio_df)


# T8

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(sfmm_t8_non_physio = rowMeans(select(., sfmm_1_t8_non_physio:sfmm_3_t8_non_physio)))

sfmm_t8_non_physio_df <- non_physio_merged_raw %>%
  select(sfmm_1_t8_non_physio:sfmm_3_t8_non_physio)

psych::alpha(sfmm_t8_non_physio_df)


```

### Rescale items for CMM

```{r}

# Rescale items from a 1-6 to a 0-5 scale

# T5 CMM assessed at T4 longitudinal

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(cmm_1_t7_non_physio:cmm_4_t7_non_physio), ~.-1))

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(across(c(cmm_1_t8_non_physio:cmm_4_t8_non_physio), ~.-1))

```



Reverse Scoring CMM

```{r}

#T7 Reverse Scoring

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(cmm_1_t7_non_physio = 5 - cmm_1_t7_non_physio,
         cmm_2_t7_non_physio = 5 - cmm_2_t7_non_physio,
         cmm_3_t7_non_physio = 5 - cmm_3_t7_non_physio,
         cmm_4_t7_non_physio = 5 - cmm_4_t7_non_physio) 


#T8 Reverse Scoring

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(cmm_1_t8_non_physio = 5 - cmm_1_t8_non_physio,
         cmm_2_t8_non_physio = 5 - cmm_2_t8_non_physio,
         cmm_3_t8_non_physio = 5 - cmm_3_t8_non_physio,
         cmm_4_t8_non_physio = 5 - cmm_4_t8_non_physio) 

```

Calculate summary scores and alphas for CMM

```{r}

# T7 

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(cmm_t7_non_physio = rowMeans(select(., cmm_1_t7_non_physio:cmm_4_t7_non_physio)))

cmm_t7_non_physio_df  <- non_physio_merged_raw %>% 
  select(cmm_1_t7_non_physio:cmm_4_t7_non_physio)

psych::alpha(cmm_t7_non_physio_df)

# T8 

non_physio_merged_raw <- non_physio_merged_raw %>%
  mutate(cmm_t8_non_physio = rowMeans(select(., cmm_1_t8_non_physio:cmm_4_t8_non_physio)))

cmm_t8_non_physio_df  <- non_physio_merged_raw %>% 
  select(cmm_1_t8_non_physio:cmm_4_t8_non_physio)

psych::alpha(cmm_t8_non_physio_df)

```

## Pandemic-Related Hardships

### Calculate summary scores and alphas

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(prh_t5_non_physio = rowSums(select(.,prh_routine_t5_non_physio:prh_income_t5_non_physio, prh_food_t5_non_physio:prh_care_t5_non_physio)))

prh_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(prh_routine_t5_non_physio:prh_income_t5_non_physio, prh_food_t5_non_physio:prh_care_t5_non_physio)

psych::alpha(prh_t5_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(prh_t8_non_physio = rowSums(select(.,prh_routine_t8_non_physio, prh_income_t8_non_physio,  prh_food_t8_non_physio, prh_housing_t8_non_physio, prh_medical_t8_non_physio, prh_mental_t8_non_physio, prh_support_t8_non_physio, prh_stress_t8_non_physio, prh_discord_t8_non_physio, prh_care_t8_non_physio)))

prh_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(prh_routine_t8_non_physio, prh_income_t8_non_physio,  prh_food_t8_non_physio, prh_housing_t8_non_physio, prh_medical_t8_non_physio, prh_mental_t8_non_physio, prh_support_t8_non_physio, prh_stress_t8_non_physio, prh_discord_t8_non_physio, prh_care_t8_non_physio)

psych::alpha(prh_t8_non_physio_df)

```

## Trait Optimism

### Rescale and reverse-code items

```{r}

# Rescale items from a 1-5 to a 0-4 scale

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(optimism_1_t8_non_physio = optimism_1_t8_non_physio - 1,
         optimism_2_t8_non_physio = optimism_2_t8_non_physio - 1)

# Reverse-score item 2

non_physio_merged_raw[ ,"optimism_2_t8_non_physio"] <- 4 - non_physio_merged_raw[ ,"optimism_2_t8_non_physio"]

```

### Calculate summary scores and alphas

```{r}

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(optimism_t8_non_physio = rowSums(select(.,optimism_1_t8_non_physio, optimism_2_t8_non_physio)))

optimism_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(optimism_1_t8_non_physio, optimism_2_t8_non_physio)

psych::alpha(optimism_t8_non_physio_df)



```

## Self-Efficacy

### Calculate summary scores and alphas

```{r}

# T5

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(self_efficacy_t5_non_physio = rowMeans(select(.,self_efficacy_1_t5_non_physio, self_efficacy_2_t5_non_physio,
                                                        self_efficacy_3_t5_non_physio)))

self_efficacy_t5_non_physio_df <- non_physio_merged_raw %>% 
  select(self_efficacy_1_t5_non_physio, self_efficacy_2_t5_non_physio,
                                                        self_efficacy_3_t5_non_physio)

psych::alpha(self_efficacy_t5_non_physio_df)

# T8

non_physio_merged_raw <- non_physio_merged_raw %>% 
  mutate(self_efficacy_t8_non_physio = rowMeans(select(.,self_efficacy_1_t8_non_physio, self_efficacy_2_t8_non_physio,
                                                        self_efficacy_3_t8_non_physio)))

self_efficacy_t8_non_physio_df <- non_physio_merged_raw %>% 
  select(self_efficacy_1_t8_non_physio, self_efficacy_2_t8_non_physio,
                                                        self_efficacy_3_t8_non_physio)

psych::alpha(self_efficacy_t8_non_physio_df)



```


# Make and export identifying key

```{r}

# Make identifying key

non_physio_id_key <- non_physio_merged_raw %>% 
  select(participant_id, RecipientEmail, Status_t5_non_physio, Progress_t5_non_physio, StartDate_t5_non_physio, EndDate_t5_non_physio, duration_t5_non_physio,
         Finished_t5_non_physio, LocationLatitude_t5_non_physio, 
         LocationLongitude_t5_non_physio, Status_t6_non_physio, Progress_t6_non_physio, StartDate_t6_non_physio, EndDate_t6_non_physio,
         duration_t6_non_physio, Finished_t6_non_physio, LocationLatitude_t6_non_physio, LocationLongitude_t6_non_physio, Status_t7_non_physio, Progress_t7_non_physio, StartDate_t7_non_physio, EndDate_t7_non_physio, duration_t7_non_physio, 
         Finished_t7_non_physio, LocationLatitude_t7_non_physio, LocationLongitude_t7_non_physio, Status_t8_non_physio, Progress_t8_non_physio, StartDate_t8_non_physio, EndDate_t8_non_physio, duration_t8_non_physio, Finished_t8_non_physio, LocationLatitude_t8_non_physio, LocationLongitude_t8_non_physio)

# Remove unnecessary identifying data from non_physio_merged_raw

non_physio_merged_raw <- non_physio_merged_raw %>% 
  select(-c(Status_t5_non_physio, Progress_t5_non_physio, StartDate_t5_non_physio, EndDate_t5_non_physio, LocationLatitude_t5_non_physio, 
         LocationLongitude_t5_non_physio, Status_t6_non_physio, Progress_t6_non_physio, StartDate_t6_non_physio, EndDate_t6_non_physio,
          LocationLatitude_t6_non_physio, LocationLongitude_t6_non_physio,
         Part.1.Vid.1.Timing_First.Click_t6_non_physio:Part.1.Vid.1.Timing_Click.Count_t6_non_physio,
         Part.1.Vid.2.Timing_First.Click_t6_non_physio:Part.1.Vid.2.Timing_Click.Count_t6_non_physio,
         Step.2.Vid.1.Time_First.Click_t6_non_physio:Step.2.Vid.1.Time_Click.Count_t6_non_physio,
         Part.2.Vid.2.Timing_First.Click_t6_non_physio:Part.2.Vid.2.Timing_Click.Count_t6_non_physio,
         Step.2.Vid.3.Time_First.Click_t6_non_physio:Step.2.Vid.3.Time_Click.Count_t6_non_physio,
         con_vid_1_time_First.Click_t6_non_physio:con_vid_2_time_Click.Count_t6_non_physio, 
         con_vid_3_time_First.Click_t6_non_physio:con_vid_3_time_Click.Count_t6_non_physio,
         con_vid_4_time_First.Click_t6_non_physio:con_vid_4_time_Click.Count_t6_non_physio,
         con_vid_5_time_First.Click_t6_non_physio:con_vid_5_time_Click.Count_t6_non_physio,
         Status_t7_non_physio, Progress_t7_non_physio, StartDate_t7_non_physio, EndDate_t7_non_physio, LocationLatitude_t7_non_physio, LocationLongitude_t7_non_physio, Status_t8_non_physio, Progress_t8_non_physio, StartDate_t8_non_physio, EndDate_t8_non_physio, LocationLatitude_t8_non_physio, LocationLongitude_t8_non_physio))

```

## Create dataframe with demographics, qualitative responses, and summary scores

```{r}

non_physio_summaries_raw <- non_physio_merged_raw %>% 
  select(RecipientEmail:vax_status_free_t5_non_physio, religion_non_physio:religion_free_t5_non_physio,
         condition, cov_sym_t7_non_physio:COVID.Status_t7_non_physio, 
         prh_routine_t8_non_physio:COVID.Vaccine.Statu_t8_non_physio, durability_1_t8_non_physio:durability_free_t8_non_physio, extraversion_t8_non_physio:dependability_t8_non_physio,
         relationships_open_t8_non_physio:self_efficacy_t8_non_physio)

```


# Write ID key to Box

```{r}

write.csv(non_physio_id_key, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ROTP Non-Physio Preprocessing/ROTP_Non_Physio_ID_Key.csv")

```


# Write merged raw dataset to Box

```{r}

write.csv(non_physio_summaries_raw, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ROTP Non-Physio Preprocessing/Preprocessed Data/ROTP_Non_Physio_Summaries_Raw.csv")

write.csv(non_physio_merged_raw, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ROTP Non-Physio Preprocessing/Preprocessed Data/ROTP_Non_Physio_Merged_Raw.csv")

```

