---
title: "ROTP Merge and Deidentify"
authorL "Jesse Barrera"
output: html_document
date: "2023-04-27"
---

# Load packages

```{r}

library (readr)
library(dplyr)
library(psych)
library(lubridate)
library(mice)
library(kutils)
library(ggplot2)
library(tidyverse)

```

# Import preprocessed data

```{r}

# Set working directory

setwd("/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses")
# Import 

longitudinal <- read.csv("COVID Longitudinal Preprocessing/Preprocessed Data/Longitudinal_Summaries_Raw.csv")


physio <- read.csv("ROTP + Physio Preprocessing/Preprocessed Data/ROTP_Physio_Summaries_Raw.csv")


non_physio <- read.csv("ROTP Non-Physio Preprocessing/Preprocessed Data/ROTP_Non_Physio_Summaries_Raw.csv")


```

# Merge datasets into wide format

```{r}

# Merge physio with longitudinal

longitudinal <- longitudinal %>% 
  rename("RecipientEmail" = "email")

physio <- physio %>% 
  mutate(participant_id = participant_id + 500)

physio_merged_wide <- left_join(physio, longitudinal, by = "RecipientEmail") %>% 
  mutate(branch = "physio") 

colnames(physio_merged_wide) <- gsub("_physio", "", colnames(physio_merged_wide))



# Merge non-physio with longitudinal

non_physio_merged_wide <- left_join(non_physio, longitudinal, by = "RecipientEmail") %>% 
  mutate(branch = "non-physio") 

colnames(non_physio_merged_wide) <- gsub("_non_physio", "", colnames(non_physio_merged_wide))


# Merge physio and non-physio together

## Find columns that are shared and not shared between physio and non-physio

shared_columns <- intersect(colnames(physio_merged_wide), colnames(non_physio_merged_wide))

unshared_columns_physio <- setdiff(colnames(physio_merged_wide), colnames(non_physio_merged_wide))

unshared_columns_non_physio <- setdiff(colnames(non_physio_merged_wide), colnames(physio_merged_wide))

# Merge shared columns together using rbind

physio_shared <- physio_merged_wide[ ,shared_columns]

non_physio_shared <- non_physio_merged_wide[ ,shared_columns]

merged_wide_shared <- rbind(physio_shared, non_physio_shared)

# Merge shared columns with unshared columns using left_join

physio_unshared <- physio_merged_wide[ ,c(unshared_columns_physio, "RecipientEmail")]

non_physio_unshared <- non_physio_merged_wide[ ,c(unshared_columns_non_physio, "RecipientEmail")]

merged_wide <- left_join(merged_wide_shared, physio_unshared, by = "RecipientEmail")

merged_wide <- left_join(merged_wide, non_physio_unshared, by = "RecipientEmail")

```

```{r}

unique(merged_wide$branch)

table(merged_wide$int_con_completion, merged_wide$condition, merged_wide$branch)

table(merged_wide$participant_retention, merged_wide$condition, merged_wide$branch)



```


# Visualize retention

```{r}

merged_wide_simplified <- merged_wide %>% 
  filter(participant_retention != "N/T6, Y/T7, N/T8") %>% 
  filter(participant_retention != "Y/T6, N/T7, Y/T8") %>% 
  filter(participant_retention != "N/T6/T7, Y/T8") %>% 
  filter(participant_retention != "N/T6, Y/T7/T8") %>% 
  filter(!is.na(participant_retention))

# Race

merged_wide_simplified_poc <- merged_wide_simplified %>% 
  filter(race_ethnicity != "White")

ggplot(merged_wide_simplified_poc, aes(x = participant_retention, fill = race_ethnicity)) +
  geom_bar(position = "dodge") + 
  facet_grid(rows = vars(condition))



# Condition

ggplot(merged_wide_simplified, aes(x = participant_retention, fill = condition)) +
  geom_bar(position = "dodge") + 
  facet_grid(rows = vars(branch))

# Gender

merged_wide_simplified_gender <- merged_wide_simplified %>% 
  filter(!is.na(gender))

ggplot(merged_wide_simplified_gender, aes(x = participant_retention, fill = gender)) +
  geom_bar(position = "dodge") +
  facet_grid(rows = vars(condition))

# Political Affiliation

merged_wide_simplified_political <- merged_wide_simplified %>% 
  filter(!is.na(political_party))

ggplot(merged_wide_simplified_political, aes(x = participant_retention, fill = political_party)) +
  geom_bar(position = "dodge") +
  facet_grid(rows = vars(condition))

```

# Make wide format dataframe excluding participants who did not complete T2

```{r}

merged_wide_treated <- merged_wide %>% 
  filter(int_con_completion == "Complete")

```



# Merge datasets into long format

```{r}

# Create separate dataframes for each timepoint

merged_t5 <- merged_wide %>% 
  select(contains("_t5")) %>% 
  mutate(RecipientEmail = merged_wide$RecipientEmail) %>% 
  mutate(timepoint = 1) 

colnames(merged_t5) <- gsub("_t5", "", colnames(merged_t5))

merged_t6 <- merged_wide %>% 
  select(contains("_t6")) %>% 
  mutate(RecipientEmail = merged_wide$RecipientEmail) %>% 
  mutate(timepoint = 2)

colnames(merged_t6) <- gsub("_t6", "", colnames(merged_t6))


merged_t7 <- merged_wide %>% 
  select(contains("_t7")) %>% 
  mutate(RecipientEmail = merged_wide$RecipientEmail) %>% 
  mutate(timepoint = 3)

colnames(merged_t7) <- gsub("_t7", "", colnames(merged_t7))


merged_t8 <- merged_wide %>% 
  select(contains("_t8")) %>% 
  mutate(RecipientEmail = merged_wide$RecipientEmail) %>% 
  mutate(timepoint = 4)

colnames(merged_t8) <- gsub("_t8", "", colnames(merged_t8))


merged_additional <- merged_wide %>% 
  select(-contains("_t5")) %>% 
  select(-contains("_t6")) %>% 
  select(-contains("_t7")) %>% 
  select(-contains("_t8"))

# Merge dataframes together in long format

## Remove timepoint identifiers

colnames(merged_t5) <- gsub("_t5", "", colnames(merged_t5))

colnames(merged_t6) <- gsub("_t6", "", colnames(merged_t6))

colnames(merged_t7) <- gsub("_t7", "", colnames(merged_t7))

colnames(merged_t8) <- gsub("_t8", "", colnames(merged_t8))

## Merge merged_t5 - merged_t8 together long

merged_long <- bind_rows(merged_t5, merged_t6, merged_t7, merged_t8)


## Merge with columns that don't change across timepoints

merged_long <- left_join(merged_long, merged_additional, by = "RecipientEmail") 


```

# Make long format dataframe excluding participants who didd not complete intervention or control

```{r}

merged_long_treated <- merged_long %>% 
  filter(int_con_completion == "Complete")

```


# Change order of columns in long dataframe

```{r}

merged_long <- merged_long %>% 
  relocate(c(participant_id, timepoint, branch, condition, int_con_completion, participant_retention, age:political_party), 
           .before = prh_routine)

merged_long_treated <- merged_long_treated %>% 
  relocate(c(participant_id, timepoint, branch, condition, int_con_completion, participant_retention, age:political_party), 
           .before = prh_routine)

```

# Deidentify long and wide dataframes

```{r}

merged_wide_deidentified <- merged_wide %>% 
  select(-(RecipientEmail)) %>% 
  arrange(participant_id)

merged_wide_deidentified_treated <- merged_wide_treated %>% 
  select(-(RecipientEmail)) %>% 
  arrange(participant_id)

merged_long_deidentified <- merged_long %>% 
  select(-c(RecipientEmail)) %>% 
  arrange(participant_id, timepoint)

merged_long_deidentified_treated <- merged_long_treated %>% 
  select(-(RecipientEmail)) %>% 
  arrange(participant_id)

```

# Export identifying keys

```{r}

# Make identifying keys

id_key_itt <- merged_wide %>% 
  select(participant_id, RecipientEmail)

id_key_treated <- merged_wide_treated %>% 
  select(participant_id, RecipientEmail)

# Write ID Keys to Box

write.csv(id_key_itt, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ID Keys/ROTP_ID_Key_Merged_ITT.csv")

write.csv(id_key_treated, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/ID Keys/ROTP_ID_Key_Merged_Treated.csv")


```

# Write deidentified datasets to Box

```{r}

# Wide dataframes

write.csv(merged_wide_deidentified, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Preprocessed Data/merged_wide_deidentified.csv")

write.csv(merged_wide_deidentified_treated, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Preprocessed Data/merged_wide_deidentified_treated.csv")

# Long dataframes

write.csv(merged_long_deidentified, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Preprocessed Data/merged_long_deidentified.csv")

write.csv(merged_long_deidentified_treated, "/Users/barreraj/Box Sync/COVID19/COVID Intervention + Physio/Analyses/Preprocessed Data/merged_long_deidentified_treated.csv")

```





